---
title: "Statistical analysis of mean fiber area by muscle and fiber type"
author: Tyler Sagendorf
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  rmarkdown::html_document:
    toc: true
bibliography: ./references.bib
csl: ./apa-numeric-superscript-brackets.csl
link-citations: yes
vignette: >
  %\VignetteIndexEntry{Statistical analyses of mean fiber area by muscle and fiber type}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5,
  message = FALSE,
  warning = FALSE
)
```

```{r setup}
# Required packages
library(MotrpacRatTrainingPhysiologyData)
library(ggplot2)
library(MASS)
library(dplyr)
library(tibble)
library(tidyr)
library(purrr)
library(emmeans)
library(nlme)
library(stats)
theme_set(theme_bw()) # base plot theme
```


# Plots

We will look at plots of mean fiber area.

## MG

```{r, fig.height=3.5, fig.width=5}
# Plot points
FIBER_TYPES %>% 
  filter(muscle == "MG") %>% 
  ggplot(aes(x = group, y = fiber_area)) +
  geom_point(na.rm = TRUE, alpha = 0.5,
             position = position_jitter(width = 0.1, height = 0)) +
  facet_grid(age + sex ~ type)
```

## LG

```{r, fig.height=3.5, fig.width=5}
# Plot points
FIBER_TYPES %>% 
  filter(muscle == "LG") %>% 
  ggplot(aes(x = group, y = fiber_area)) +
  geom_point(na.rm = TRUE, alpha = 0.5,
             position = position_jitter(width = 0.1, height = 0)) +
  facet_grid(age + sex ~ type)
```

## PL

```{r, fig.height=3.5, fig.width=5}
# Plot points
FIBER_TYPES %>% 
  filter(muscle == "PL") %>% 
  ggplot(aes(x = group, y = fiber_area)) +
  geom_point(na.rm = TRUE, alpha = 0.5,
             position = position_jitter(width = 0.1, height = 0)) +
  facet_grid(age + sex ~ type)
```

## SOL

```{r, fig.height=3.5, fig.width=3.5}
# Plot points
FIBER_TYPES %>% 
  filter(muscle == "SOL") %>% 
  ggplot(aes(x = group, y = fiber_area)) +
  geom_point(na.rm = TRUE, alpha = 0.5,
             position = position_jitter(width = 0.1, height = 0)) +
  facet_grid(age + sex ~ type)
```


# Regression Models

We will check the mean-variance relationship.

```{r}
mv <- FIBER_TYPES %>% 
  group_by(sex, group, age, muscle, type) %>% 
  summarise(mn = mean(fiber_area, na.rm = TRUE),
            vr = var(fiber_area, na.rm = TRUE))

fit.mv <- lm(log(vr) ~ log(mn), data = mv)
coef(fit.mv)
```

```{r, fig.height=4, fig.width=5}
plot(log(vr) ~ log(mn), data = mv, las = 1, pch = 19, 
     xlab = "log(group means)", ylab = "log(group variances)")
abline(coef(fit.mv), lwd = 2)
```

The slope of the line is close to 2, which suggests a gamma distribution or log transformation may be appropriate. Since SOL only consists of type I and IIa fibers, we can not include an interaction between `muscle` and `type`, since it will be inestimable for SOL type IIb and IIx. Instead, we will create a new `muscle_type` variable by concatenating `muscle` and `type`.

```{r}
FIBER_TYPES <- mutate(FIBER_TYPES, muscle_type = paste0(muscle, ".", type))

fit.area <- lme(
  fixed = log(fiber_area) ~ age * sex * group * muscle_type,
  random = ~ 1 | pid,
  data = FIBER_TYPES,
  na.action = na.exclude)
```

```{r fig.height=5, fig.width=6}
r <- resid(fit.area, scaled = TRUE, type = "pearson")

par(mfrow = c(2, 2))
# Standardized residuals vs. fitted plot
plot(x = fitted(fit.area), y = r, 
     ylab = "Standardized residuals", xlab = "Fitted values")
lines(loess.smooth(x = fitted(fit.area), y = r, degree = 2),
      col = "red", lwd = 2)

# Scale-location plot
plot(x = fitted(fit.area), y = sqrt(abs(r)),
     ylab = "sqrt(|standardized residuals|)", xlab = "Fitted values")
lines(loess.smooth(x = fitted(fit.area), y = sqrt(abs(r)), degree = 2),
      col = "red", lwd = 2)

# Normal Q-Q plot
qqnorm(r); qqline(r, col = "red")
par(mfrow = c(1, 1))
```

```{r}
# Residuals vs. predictor levels
par(mfrow = c(2, 3), mar = c(5, 3, 0.5, 0.5))
boxplot(r ~ age, data = FIBER_TYPES, ylab = "")
boxplot(r ~ group, data = FIBER_TYPES, ylab = "")
boxplot(r ~ sex, data = FIBER_TYPES, ylab = "")
boxplot(r ~ muscle, data = FIBER_TYPES, ylab = "")
boxplot(r ~ type, data = FIBER_TYPES, ylab = "")
mtext("Standardized residuals", side = 2, line = -1, outer = TRUE)
par(mfrow = c(1, 1), mar = c(5, 4, 4, 2))
```

The diagnostic plots look fine. We will try to simplify the model.

```{r}
anova(fit.area)
```

```{r}
fit.area.1 <- update(fit.area, 
                     fixed = . ~ (age + sex + group + muscle_type) ^ 3 -
                       sex:group:muscle_type)
anova(fit.area, fit.area.1)
```

Removal of the 4-way interaction and the least significant 3-way interaction leads to a significant difference (P = 0.13) between the full and reduced models, so we will not remove any terms.

```{r}
VarCorr(fit.area)
```


# Hypothesis Testing

We will compare the 8W trained to the sedentary control group within each age, sex, and muscle. We will then adjust p-values across fiber types within each age, sex, and muscle group using the Holm method.

```{r}
# Estimated marginal means
FIBER_AREA_EMM <- emmeans(fit.area, specs = "group", 
                          by = c("age", "sex", "muscle_type"),
                          type = "response", infer = TRUE)
```

```{r}
# Extract model info
model_df <- data.frame(response = "Mean Fiber Area",
                       model = paste(deparse(fit.area[["call"]]), 
                                     collapse = "")) %>% 
  mutate(model = gsub("(?<=[\\s])\\s*|^\\s+|\\s+$", "", model, perl = TRUE),
         model.type = "lme",
         fixed = sub(".*fixed = ([^,]+),.*", "\\1", model),
         random = "~ 1 | pid") %>% 
  dplyr::select(-model)

FIBER_AREA_STATS <- FIBER_AREA_EMM %>% 
  contrast(method = "trt.vs.ctrl") %>% 
  summary(infer = TRUE) %>% 
  as.data.frame() %>% 
  rename(any_of(c(lower.CL = "asymp.LCL",
                  upper.CL = "asymp.UCL"))) %>% 
  separate_wider_delim(cols = muscle_type, delim = ".", 
                       names = c("muscle", "type")) %>%
  mutate(muscle = factor(muscle, levels = c("LG", "MG", "PL", "SOL")),
         type = factor(type, levels = c("I", "IIa", "IIx", "IIb"))) %>% 
  # Holm-adjust p-values across fiber types
  group_by(age, sex, muscle) %>% 
  mutate(p.adj = p.adjust(p.value, method = "holm"),
         signif = ifelse(p.adj < 0.05, "*", "")) %>%
  ungroup() %>% 
  mutate(response = "Mean Fiber Area") %>% 
  left_join(model_df, by = "response") %>% 
  pivot_longer(cols = contains(".ratio"), 
               names_to = "statistic.type", 
               values_to = "statistic", 
               values_drop_na = TRUE) %>% 
  mutate(across(.cols = c(ratio, lower.CL, upper.CL, statistic), 
                .fns = ~ round(.x, digits = 2)),
         across(.cols = c(SE, p.value, p.adj),
                .fns = ~ signif(.x, digits = 2))) %>% 
  relocate(c(starts_with("statistic"), p.value), .before = p.adj) %>% 
  relocate(signif, .after = p.adj) %>% 
  relocate(response, .before = everything()) %>% 
  relocate(contrast, .before = ratio) %>% 
  arrange(response, age, sex, muscle, type)
```

See `?FIBER_AREA_STATS` for details.

```{r}
print.data.frame(head(FIBER_AREA_STATS))
```

```{r, eval=FALSE, include=FALSE}
# Save data
usethis::use_data(FIBER_AREA_EMM, internal = FALSE, overwrite = TRUE,
                  compress = "bzip2", version = 3)

usethis::use_data(FIBER_AREA_STATS, internal = FALSE, overwrite = TRUE,
                  compress = "bzip2", version = 3)
```


# Session Info

```{r}
sessionInfo()
```


# References

