---
title: "Plots of plasma clinical analytes"
author: Tyler Sagendorf
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  rmarkdown::html_document:
    code_folding: hide
    toc: true
    toc_depth: 2
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 1.5,
  fig.height = 1.8,
  out.height = "50%",
  out.width = "50%",
  dpi = 400,
  message = FALSE,
  warning = FALSE
)

save_plots <- dir.exists(paths = file.path("..", "..", "plots"))
```

```{r setup}
# Required packages
library(MotrpacRatTrainingPhysiologyData)
library(dplyr)
library(tibble)
library(tidyr)
library(purrr)
library(ggplot2)
library(latex2exp)
```

# Overview

This article generates all plasma clinical analyte figures. A bracket indicates a significant difference (Dunnett's test p-value < 0.05) between the means of the SED group and a trained group (1W, 2W, 4W, 8W). Plots are generated for each combination of age and sex and such that the y-axis limits for the same analyte are identical. This allows for easier visual comparisons. Please refer to the "Statistical analyses of plasma clinical analytes" vignette for code to generate `ANALYTES_STATS`.

**Data Preparation:**

We apply the `summary` method to each `emmGrid` object and rename columns to work with `plot_baseline`. Since the formula for corticosterone did not include `age` as a predictor, the entries for the `age` column are `NA`. We instead modify these entries to include both levels of `age` separated by a comma. Using this, we can separate the rows to effectively duplicate the results so that we now have corticosterone data for both ages. Lastly, we ensure that `group` is a factor to preserve the order when plotting. This list of objects is then converted to a single `data.frame` with the `response` column specifying which analyte is being tested.

```{r}
# Reformat confidence interval data
conf_df <- map(ANALYTES_EMM, function(emm_i) {
  terms_i <- attr(terms(emm_i@model.info), which = "term.labels")
  
  out <- summary(emm_i) %>% 
    as.data.frame() %>% 
    rename(any_of(c(lower.CL = "asymp.LCL",
                    upper.CL = "asymp.UCL",
                    response_mean = "response",
                    response_mean = "rate")))
  
  # In some cases, age or sex is not included in the model, so their entries
  # would be NA. We will instead duplicate those rows for plotting.
  # This was already done for ANALYTES_STATS.
  if (!"age" %in% colnames(out)) {
    out$age <- "6M, 18M"
  }
  
  out <- out %>% 
    separate_longer_delim(cols = age, delim = ", ") %>% 
    mutate(group = factor(group, levels = c("SED", paste0(2 ^ (0:3), "W"))))
  
  return(out)
}) %>% 
  enframe(name = "response") %>% 
  unnest(value)
```


# Corticosterone

Corticosterone (ng/mL).

## 6M Female

```{r}
plot_baseline(ANALYTES, 
              response = "corticosterone", 
              conf = filter(conf_df, response == "Corticosterone"),
              stats = filter(ANALYTES_STATS, response == "Corticosterone"),
              sex = "Female", age = "6M") +
  scale_y_continuous(name = "Corticosterone (ng/mL)",
                     breaks = seq(0, 170, 40),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 170), clip = "off") +
  theme(plot.margin = unit(c(20, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_corticosterone_6M_female.pdf"),
       height = 1.8, width = 1.5, family = "ArialMT")
```

## 6M Male

```{r}
plot_baseline(ANALYTES, 
              response = "corticosterone", 
              conf = filter(conf_df, response == "Corticosterone"),
              stats = filter(ANALYTES_STATS, 
                             response == "Corticosterone"),
              sex = "Male", age = "6M", y_position = 145) +
  scale_y_continuous(name = "Corticosterone (ng/mL)",
                     breaks = seq(0, 170, 40),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 170), clip = "off") +
  theme(plot.margin = unit(c(20, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_corticosterone_6M_male.pdf"),
       height = 1.8, width = 1.5, family = "ArialMT")
```

## 18M Female

```{r}
plot_baseline(ANALYTES, 
              response = "corticosterone", 
              conf = filter(conf_df, response == "Corticosterone"),
              stats = filter(ANALYTES_STATS, 
                             response == "Corticosterone"),
              sex = "Female", age = "18M", y_position = 75) +
  scale_y_continuous(name = "Corticosterone (ng/mL)",
                     breaks = seq(0, 170, 40),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 170), clip = "off") +
  theme(plot.margin = unit(c(20, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_corticosterone_18M_female.pdf"),
       height = 1.8, width = 1.5, family = "ArialMT")
```

## 18M Male

```{r}
plot_baseline(ANALYTES, 
              response = "corticosterone", 
              conf = filter(conf_df, response == "Corticosterone"),
              stats = filter(ANALYTES_STATS, 
                             response == "Corticosterone"),
              sex = "Male", age = "18M") +
  scale_y_continuous(name = "Corticosterone (ng/mL)",
                     breaks = seq(0, 170, 40),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 170), clip = "off") +
  theme(plot.margin = unit(c(20, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_corticosterone_18M_male.pdf"),
       height = 1.8, width = 1.5, family = "ArialMT")
```


# Glucagon

Glucagon (pM).

## 6M Female

```{r}
plot_baseline(ANALYTES, 
              response = "glucagon", 
              conf = filter(conf_df, response == "Glucagon"),
              stats = filter(ANALYTES_STATS, response == "Glucagon"),
              sex = "Female", age = "6M") +
  scale_y_continuous(name = "Glucagon (pM)",
                     breaks = seq(0, 160, 40),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 162), clip = "off") +
  theme(plot.margin = unit(c(8, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_glucagon_6M_female.pdf"),
       height = 1.8, width = 1.5, family = "ArialMT")
```

## 6M Male

```{r}
plot_baseline(ANALYTES, 
              response = "glucagon", 
              conf = filter(conf_df, response == "Glucagon"),
              stats = filter(ANALYTES_STATS, response == "Glucagon"),
              sex = "Male", age = "6M") +
  scale_y_continuous(name = "Glucagon (pM)",
                     breaks = seq(0, 160, 40),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 162), clip = "off") +
  theme(plot.margin = unit(c(8, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_glucagon_6M_male.pdf"),
       height = 1.8, width = 1.5, family = "ArialMT")
```

## 18M Female

```{r}
plot_baseline(ANALYTES, 
              response = "glucagon", 
              conf = filter(conf_df, response == "Glucagon"),
              stats = filter(ANALYTES_STATS, response == "Glucagon"),
              sex = "Female", age = "18M") +
  scale_y_continuous(name = "Glucagon (pM)",
                     breaks = seq(0, 160, 40),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 162), clip = "off") +
  theme(plot.margin = unit(c(8, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_glucagon_18M_female.pdf"),
       height = 1.8, width = 1.5, family = "ArialMT")
```

## 18M Male

```{r}
plot_baseline(ANALYTES, 
              response = "glucagon", 
              conf = filter(conf_df, response == "Glucagon"),
              stats = filter(ANALYTES_STATS, response == "Glucagon"),
              sex = "Male", age = "18M") +
  scale_y_continuous(name = "Glucagon (pM)",
                     breaks = seq(0, 160, 40),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 162), clip = "off") +
  theme(plot.margin = unit(c(8, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_glucagon_18M_male.pdf"),
       height = 1.8, width = 1.5, family = "ArialMT")
```


# Glucose

Glucose (mg/dL).

## 6M Female

```{r}
plot_baseline(ANALYTES, 
              response = "glucose", 
              conf = filter(conf_df, response == "Glucose"),
              stats = filter(ANALYTES_STATS, response == "Glucose"),
              sex = "Female", age = "6M") +
  scale_y_continuous(name = "Glucose (mg/dL)",
                     breaks = seq(110, 230, 20),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(110, 230), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_glucose_6M_female.pdf"),
       height = 1.8, width = 1.2, family = "ArialMT")
```

## 6M Male

```{r}
plot_baseline(ANALYTES, 
              response = "glucose", 
              conf = filter(conf_df, response == "Glucose"),
              stats = filter(ANALYTES_STATS, response == "Glucose"),
              sex = "Male", age = "6M") +
  scale_y_continuous(name = "Glucose (mg/dL)",
                     breaks = seq(110, 230, 20),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(110, 230), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_glucose_6M_male.pdf"),
       height = 1.8, width = 1.2, family = "ArialMT")
```

## 18M Female

```{r}
plot_baseline(ANALYTES, 
              response = "glucose", 
              conf = filter(conf_df, response == "Glucose"),
              stats = filter(ANALYTES_STATS, response == "Glucose"),
              sex = "Female", age = "18M") +
  scale_y_continuous(name = "Glucose (mg/dL)",
                     breaks = seq(110, 230, 20),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(110, 230), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_glucose_18M_female.pdf"),
       height = 1.8, width = 1.2, family = "ArialMT")
```

## 18M Male

```{r}
plot_baseline(ANALYTES, 
              response = "glucose", 
              conf = filter(conf_df, response == "Glucose"),
              stats = filter(ANALYTES_STATS, response == "Glucose"),
              sex = "Male", age = "18M", y_position = 204) +
  scale_y_continuous(name = "Glucose (mg/dL)",
                     breaks = seq(110, 230, 20),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(110, 230), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_glucose_18M_male.pdf"),
       height = 1.8, width = 1.2, family = "ArialMT")
```


# Glycerol

## 6M Female

```{r}
plot_baseline(ANALYTES, 
              response = "glycerol", 
              conf = filter(conf_df, response == "Glycerol"),
              stats = filter(ANALYTES_STATS, response == "Glycerol"),
              sex = "Female", age = "6M") +
  scale_y_continuous(name = "Glycerol (mg/dL)",
                     breaks = seq(0, 2.5, 0.5),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 2.7), clip = "off") +
  theme(plot.margin = unit(c(10, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_glycerol_6M_female.pdf"),
       height = 1.8, width = 1.2, family = "ArialMT")
```

## 6M Male

```{r}
plot_baseline(ANALYTES, 
              response = "glycerol", 
              conf = filter(conf_df, response == "Glycerol"),
              stats = filter(ANALYTES_STATS, response == "Glycerol"),
              sex = "Male", age = "6M") +
  scale_y_continuous(name = "Glycerol (mg/dL)",
                     breaks = seq(0, 2.5, 0.5),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 2.7), clip = "off") +
  theme(plot.margin = unit(c(10, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_glycerol_6M_male.pdf"),
       height = 1.8, width = 1.2, family = "ArialMT")
```

## 18M Female

```{r}
plot_baseline(ANALYTES, 
              response = "glycerol", 
              conf = filter(conf_df, response == "Glycerol"),
              stats = filter(ANALYTES_STATS, response == "Glycerol"),
              sex = "Female", age = "18M") +
  scale_y_continuous(name = "Glycerol (mg/dL)",
                     breaks = seq(0, 2.5, 0.5),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 2.7), clip = "off") +
  theme(plot.margin = unit(c(10, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_glycerol_18M_female.pdf"),
       height = 1.8, width = 1.2, family = "ArialMT")
```

## 18M Male

```{r}
plot_baseline(ANALYTES, 
              response = "glycerol", 
              conf = filter(conf_df, response == "Glycerol"),
              stats = filter(ANALYTES_STATS, response == "Glycerol"),
              sex = "Male", age = "18M") +
  scale_y_continuous(name = "Glycerol (mg/dL)",
                     breaks = seq(0, 2.5, 0.5),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 2.7), clip = "off") +
  theme(plot.margin = unit(c(10, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_glycerol_18M_male.pdf"),
       height = 1.8, width = 1.2, family = "ArialMT")
```


# Insulin

## 6M Female

```{r}
plot_baseline(ANALYTES, 
              response = "insulin_pm", 
              conf = filter(conf_df, response == "Insulin"),
              stats = filter(ANALYTES_STATS, response == "Insulin"),
              sex = "Female", age = "6M") +
  scale_y_continuous(name = "Insulin (pM)",
                     breaks = seq(0, 1400, 200),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 1400), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_insulin_6M_female.pdf"),
       height = 1.8, width = 1.5, family = "ArialMT")
```

## 6M Male

```{r}
plot_baseline(ANALYTES, 
              response = "insulin_pm", 
              conf = filter(conf_df, response == "Insulin"),
              stats = filter(ANALYTES_STATS, response == "Insulin"),
              sex = "Male", age = "6M", y_position = 970) +
  scale_y_continuous(name = "Insulin (pM)",
                     breaks = seq(0, 1400, 200),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 1400), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_insulin_6M_male.pdf"),
       height = 1.8, width = 1.5, family = "ArialMT")
```

## 18M Female

```{r}
plot_baseline(ANALYTES, 
              response = "insulin_pm", 
              conf = filter(conf_df, response == "Insulin"),
              stats = filter(ANALYTES_STATS, response == "Insulin"),
              sex = "Female", age = "18M") +
  scale_y_continuous(name = "Insulin (pM)",
                     breaks = seq(0, 1400, 200),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 1400), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_insulin_18M_female.pdf"),
       height = 1.8, width = 1.5, family = "ArialMT")
```

## 18M Male

```{r}
plot_baseline(ANALYTES, 
              response = "insulin_pm", 
              conf = filter(conf_df, response == "Insulin"),
              stats = filter(ANALYTES_STATS, response == "Insulin"),
              sex = "Male", age = "18M", y_position = 940) +
  scale_y_continuous(name = "Insulin (pM)",
                     breaks = seq(0, 1400, 200),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 1400), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_insulin_18M_male.pdf"),
       height = 1.8, width = 1.5, family = "ArialMT")
```


# Ketones

Ketones ($\mu$mol/L).

## 6M Female

```{r}
plot_baseline(ANALYTES, 
              response = "ketones", 
              conf = filter(conf_df, response == "Ketones"),
              stats = filter(ANALYTES_STATS, response == "Ketones"),
              sex = "Female", age = "6M") +
  scale_y_continuous(name = TeX("Ketones ($\\mu$mol/L)"),
                     breaks = seq(0, 1400, 200),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 1450), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_ketones_6M_female.pdf"),
       height = 1.8, width = 1.2, family = "ArialMT")
```


## 6M Male

```{r}
plot_baseline(ANALYTES, 
              response = "ketones", 
              conf = filter(conf_df, response == "Ketones"),
              stats = filter(ANALYTES_STATS, response == "Ketones"),
              sex = "Male", age = "6M") +
  scale_y_continuous(name = TeX("Ketones ($\\mu$mol/L)"),
                     breaks = seq(0, 1400, 200),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 1450), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_ketones_6M_male.pdf"),
       height = 1.8, width = 1.2, family = "ArialMT")
```


## 18M Female

```{r}
plot_baseline(ANALYTES, 
              response = "ketones",  
              conf = filter(conf_df, response == "Ketones"),
              stats = filter(ANALYTES_STATS, response == "Ketones"),
              sex = "Female", age = "18M") +
  labs(y = TeX("Ketones ($\\mu$mol/L)")) +
  scale_y_continuous(name = TeX("Ketones ($\\mu$mol/L)"),
                     breaks = seq(0, 1400, 200),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 1450), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_ketones_18M_female.pdf"),
       height = 1.8, width = 1.2, family = "ArialMT")
```

## 18M Male

```{r}
plot_baseline(ANALYTES, 
              response = "ketones",  
              conf = filter(conf_df, response == "Ketones"),
              stats = filter(ANALYTES_STATS, response == "Ketones"),
              sex = "Male", age = "18M") +
  scale_y_continuous(name = TeX("Ketones ($\\mu$mol/L)"),
                     breaks = seq(0, 1400, 200),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 1450), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_ketones_18M_male.pdf"),
       height = 1.8, width = 1.2, family = "ArialMT")
```


# Lactate

Lactate (mmol/L).

## 6M Female

```{r}
plot_baseline(ANALYTES, 
              response = "lactate", 
              conf = filter(conf_df, response == "Lactate"),
              stats = filter(ANALYTES_STATS, response == "Lactate"),
              sex = "Female", age = "6M", y_position = 1.85) +
  scale_y_continuous(name = "Lactate (mmol/L)",
                     breaks = seq(0, 3, 0.5),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 3), clip = "off") +
  theme(plot.margin = unit(c(12, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_lactate_6M_female.pdf"),
       height = 1.8, width = 1.2, family = "ArialMT")
```

## 6M Male

```{r}
plot_baseline(ANALYTES, 
              response = "lactate", 
              conf = filter(conf_df, response == "Lactate"),
              stats = filter(ANALYTES_STATS, response == "Lactate"),
              sex = "Male", age = "6M") +
  scale_y_continuous(name = "Lactate (mmol/L)",
                     breaks = seq(0, 3, 0.5),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 3), clip = "off") +
  theme(plot.margin = unit(c(12, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_lactate_6M_male.pdf"),
       height = 1.8, width = 1.2, family = "ArialMT")
```

## 18M Female

```{r}
plot_baseline(ANALYTES, 
              response = "lactate", 
              conf = filter(conf_df, response == "Lactate"),
              stats = filter(ANALYTES_STATS, response == "Lactate"),
              sex = "Female", age = "18M", y_position = 2.25) +
  scale_y_continuous(name = "Lactate (mmol/L)",
                     breaks = seq(0, 3, 0.5),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 3), clip = "off") +
  theme(plot.margin = unit(c(12, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_lactate_18M_female.pdf"),
       height = 1.8, width = 1.2, family = "ArialMT")
```

## 18M Male

```{r}
plot_baseline(ANALYTES, 
              response = "lactate", 
              conf = filter(conf_df, response == "Lactate"),
              stats = filter(ANALYTES_STATS, response == "Lactate"),
              sex = "Male", age = "18M", y_position = 2) +
  scale_y_continuous(name = "Lactate (mmol/L)",
                     breaks = seq(0, 3, 0.5),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 3), clip = "off") +
  theme(plot.margin = unit(c(12, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_lactate_18M_male.pdf"),
       height = 1.8, width = 1.2, family = "ArialMT")
```


# Leptin

Leptin (pg/mL).

## 6M Female

```{r}
plot_baseline(ANALYTES, 
              response = "leptin", 
              conf = filter(conf_df, response == "Leptin"),
              stats = filter(ANALYTES_STATS, response == "Leptin"),
              sex = "Female", age = "6M", y_position = 3.1e4, 
              step_increase = 0.12) +
  scale_y_continuous(name = "Leptin (pg/mL)", 
                     labels = scales::label_scientific(),
                     breaks = seq(0, 7e4, 2e4),
                     limits = c(0, 7e4),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(clip = "off", ylim = c(0, 7e4)) +
  theme(plot.margin = unit(c(12, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_leptin_6M_female.pdf"),
       height = 1.8, width = 1.5, family = "ArialMT")
```

## 6M Male

```{r}
plot_baseline(ANALYTES, 
              response = "leptin", 
              conf = filter(conf_df, response == "Leptin"),
              stats = filter(ANALYTES_STATS, response == "Leptin"),
              sex = "Male", age = "6M") +
  scale_y_continuous(name = "Leptin (pg/mL)", 
                     labels = scales::label_scientific(),
                     breaks = seq(0, 7e4, 2e4),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 7e4), clip = "off") +
  theme(plot.margin = unit(c(12, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_leptin_6M_male.pdf"),
       height = 1.8, width = 1.5, family = "ArialMT")
```

## 18M Female

```{r}
plot_baseline(ANALYTES, 
              response = "leptin", 
              conf = filter(conf_df, response == "Leptin"),
              stats = filter(ANALYTES_STATS, response == "Leptin"),
              sex = "Female", age = "18M") +
  scale_y_continuous(name = "Leptin (pg/mL)", 
                     labels = scales::label_scientific(),
                     breaks = seq(0, 7e4, 2e4),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 7e4), clip = "off") +
  theme(plot.margin = unit(c(12, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_leptin_18M_female.pdf"),
       height = 1.8, width = 1.5, family = "ArialMT")
```

## 18M Male

```{r}
plot_baseline(ANALYTES, 
              response = "leptin", 
              conf = filter(conf_df, response == "Leptin"),
              stats = filter(ANALYTES_STATS, response == "Leptin"),
              sex = "Male", age = "18M", y_position = 6e4) +
  scale_y_continuous(name = "Leptin (pg/mL)", 
                     labels = scales::label_scientific(),
                     breaks = seq(0, 7e4, 2e4),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 7e4), clip = "off") +
  theme(plot.margin = unit(c(12, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_leptin_18M_male.pdf"),
       height = 1.8, width = 1.5, family = "ArialMT")
```


# NEFA

NEFA (mmol/L).

## 6M Female

```{r}
plot_baseline(ANALYTES, 
              response = "nefa", 
              conf = filter(conf_df, response == "NEFA"), 
              stats = filter(ANALYTES_STATS, response == "NEFA"),
              sex = "Female", age = "6M", y_position = 1.25) +
  scale_y_continuous(name = "NEFA (mmol/L)",
                     breaks = seq(0, 1.3, 0.2),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 1.34), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_NEFA_6M_female.pdf"),
       height = 1.8, width = 1.2, family = "ArialMT")
```

## 6M Male

```{r}
plot_baseline(ANALYTES, 
              response = "nefa", 
              conf = filter(conf_df, response == "NEFA"),
              stats = filter(ANALYTES_STATS, response == "NEFA"),
              sex = "Male", age = "6M") +
  scale_y_continuous(name = "NEFA (mmol/L)",
                     breaks = seq(0, 1.3, 0.2),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 1.34), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_NEFA_6M_male.pdf"),
       height = 1.8, width = 1.2, family = "ArialMT")
```

## 18M Female

```{r}
plot_baseline(ANALYTES, 
              response = "nefa", 
              conf = filter(conf_df, response == "NEFA"),
              stats = filter(ANALYTES_STATS, response == "NEFA"),
              sex = "Female", age = "18M", y_position = 1.15) +
  scale_y_continuous(name = "NEFA (mmol/L)",
                     breaks = seq(0, 1.3, 0.2),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 1.34), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_NEFA_18M_female.pdf"),
       height = 1.8, width = 1.2, family = "ArialMT")
```

## 18M Male

```{r}
plot_baseline(ANALYTES, 
              response = "nefa",
              conf = filter(conf_df, response == "NEFA"), 
              stats = filter(ANALYTES_STATS, response == "NEFA"),
              sex = "Male", age = "18M") +
  scale_y_continuous(name = "NEFA (mmol/L)",
                     breaks = seq(0, 1.3, 0.2),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 1.34), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "analytes_NEFA_18M_male.pdf"),
       height = 1.8, width = 1.2, family = "ArialMT")
```

