---
title: "Plots of baseline measures"
author: Tyler Sagendorf
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  rmarkdown::html_document:
    code_folding: hide
    toc: true
    toc_depth: 2
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 1.5,
  fig.height = 1.8,
  out.height = "50%",
  out.width = "50%",
  dpi = 400,
  message = FALSE,
  warning = FALSE
)
```

```{r setup}
# Required packages
library(MotrpacRatTrainingPhysiologyData)
library(dplyr)
library(tibble)
library(tidyr)
library(purrr)
library(ggplot2)
library(latex2exp)
library(ggpubr)
```

```{r}
# Reformat confidence interval data
conf_df <- map(BASELINE_EMM, function(emm_i) {
  terms_i <- attr(terms(emm_i@model.info), which = "term.labels")
  
  out <- summary(emm_i) %>% 
    as.data.frame() %>% 
    rename(any_of(c(lower.CL = "asymp.LCL",
                    upper.CL = "asymp.UCL",
                    response_mean = "response",
                    response_mean = "rate")))
  
  if ("age_group" %in% terms_i) {
    out <- mutate(out,
                  age = sub("_.*", "", age_group),
                  group = sub(".*_", "", age_group),
                  age_group = NULL)
  }
  
  out <- out %>% 
    mutate(group = factor(group, 
                          levels = c("SED", paste0(2 ^ (0:3), "W"))))
  
  return(out)
}) %>% 
  enframe(name = "response") %>% 
  unnest(value)
```


# NMR Body Mass {.tabset}

## 6M Female

```{r}
plot_baseline(x = NMR, response = "pre_weight",
              conf = filter(conf_df, response == "NMR Weight"),
              stats = filter(BASELINE_STATS, response == "NMR Weight"),
              sex = "Female", age = "6M", y_position = 207) +
  labs(y  = "NMR Body Mass (g)")

ggsave("../../plots/baseline_NMR_weight_6M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```

## 6M Male

```{r}
plot_baseline(x = NMR, response = "pre_weight",
              conf = filter(conf_df, response == "NMR Weight"),
              stats = filter(BASELINE_STATS, response == "NMR Weight"),
              sex = "Male", age = "6M", y_position = 415) +
  labs(y  = "NMR Body Mass (g)")

ggsave("../../plots/baseline_NMR_weight_6M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```

## 18M Female

```{r}
plot_baseline(x = NMR, response = "pre_weight",
              conf = filter(conf_df, response == "NMR Weight"),
              stats = filter(BASELINE_STATS, response == "NMR Weight"),
              sex = "Female", age = "18M", y_position = 265) +
  labs(y  = "NMR Body Mass (g)")

ggsave("../../plots/baseline_NMR_weight_18M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```

## 18M Male

```{r}
plot_baseline(x = NMR, response = "pre_weight",
              conf = filter(conf_df, response == "NMR Weight"),
              stats = filter(BASELINE_STATS, response == "NMR Weight"),
              sex = "Male", age = "18M") +
  labs(y  = "NMR Body Mass (g)")

ggsave("../../plots/baseline_NMR_weight_18M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```

# NMR Lean Mass {.tabset}

## 6M Female

```{r}
plot_baseline(x = NMR, response = "pre_lean",
              conf = filter(conf_df, response == "NMR Lean Mass"),
              stats = filter(BASELINE_STATS, response == "NMR Lean Mass"),
              sex = "Female", age = "6M", y_position = 123) +
  labs(y  = "NMR Lean Mass (g)")

ggsave("../../plots/baseline_NMR_lean_6M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```

## 6M Male

```{r}
plot_baseline(x = NMR, response = "pre_lean",
              conf = filter(conf_df, response == "NMR Lean Mass"),
              stats = filter(BASELINE_STATS, response == "NMR Lean Mass"),
              sex = "Male", age = "6M") +
  labs(y  = "NMR Lean Mass (g)")

ggsave("../../plots/baseline_NMR_lean_6M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```

## 18M Female

```{r}
plot_baseline(x = NMR, response = "pre_lean",
              conf = filter(conf_df, response == "NMR Lean Mass"),
              stats = filter(BASELINE_STATS, response == "NMR Lean Mass"),
              sex = "Female", age = "18M", y_position = 146) +
  labs(y  = "NMR Lean Mass (g)")

ggsave("../../plots/baseline_NMR_lean_18M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```

## 18M Male

```{r}
plot_baseline(x = NMR, response = "pre_lean",
              conf = filter(conf_df, response == "NMR Lean Mass"),
              stats = filter(BASELINE_STATS, response == "NMR Lean Mass"),
              sex = "Male", age = "18M") +
  labs(y  = "NMR Lean Mass (g)")

ggsave("../../plots/baseline_NMR_lean_18M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```


# NMR Fat Mass {.tabset}

## 6M Female

```{r}
plot_baseline(x = NMR, response = "pre_fat",
              conf = filter(conf_df, response == "NMR Fat Mass"),
              stats = filter(BASELINE_STATS, response == "NMR Fat Mass"),
              sex = "Female", age = "6M") +
  labs(y  = "NMR Fat Mass (g)")

ggsave("../../plots/baseline_NMR_fat_6M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```

## 6M Male

```{r}
plot_baseline(x = NMR, response = "pre_fat",
              conf = filter(conf_df, response == "NMR Fat Mass"),
              stats = filter(BASELINE_STATS, response == "NMR Fat Mass"),
              sex = "Male", age = "6M") +
  labs(y  = "NMR Fat Mass (g)")

ggsave("../../plots/baseline_NMR_fat_6M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```


## 18M Female

```{r}
plot_baseline(x = NMR, response = "pre_fat",
              conf = filter(conf_df, response == "NMR Fat Mass"),
              stats = filter(BASELINE_STATS, response == "NMR Fat Mass"),
              sex = "Female", age = "18M", y_position = 57) +
  labs(y  = "NMR Fat Mass (g)")

ggsave("../../plots/baseline_NMR_fat_18M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```


## 18M Male

```{r}
plot_baseline(x = NMR, response = "pre_fat",
              conf = filter(conf_df, response == "NMR Fat Mass"),
              stats = filter(BASELINE_STATS, response == "NMR Fat Mass"),
              sex = "Male", age = "18M") +
  labs(y  = "NMR Fat Mass (g)")

ggsave("../../plots/baseline_NMR_fat_18M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```


# NMR % Lean {.tabset}

## 6M Female

```{r}
plot_baseline(x = NMR, response = "pre_lean_pct",
              conf = filter(conf_df, response == "NMR % Lean"),
              stats = filter(BASELINE_STATS, response == "NMR % Lean"),
              sex = "Female", age = "6M") +
  labs(y  = "NMR % Lean Mass")

ggsave("../../plots/baseline_NMR_pct_lean_6M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```

## 6M Male

```{r}
plot_baseline(x = NMR, response = "pre_lean_pct",
              conf = filter(conf_df, response == "NMR % Lean"),
              stats = filter(BASELINE_STATS, response == "NMR % Lean"),
              sex = "Male", age = "6M") +
  labs(y  = "NMR % Lean Mass")

ggsave("../../plots/baseline_NMR_pct_lean_6M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```

## 18M Female

```{r}
plot_baseline(x = NMR, response = "pre_lean_pct",
              conf = filter(conf_df, response == "NMR % Lean"),
              stats = filter(BASELINE_STATS, response == "NMR % Lean"),
              sex = "Female", age = "18M", y_position = 57.4) +
  labs(y  = "NMR % Lean Mass")

ggsave("../../plots/baseline_NMR_pct_lean_18M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```

## 18M Male

```{r}
plot_baseline(x = NMR, response = "pre_lean_pct",
              conf = filter(conf_df, response == "NMR % Lean"),
              stats = filter(BASELINE_STATS, response == "NMR % Lean"),
              sex = "Male", age = "18M", y_position = 55.7) +
  labs(y  = "NMR % Lean Mass")

ggsave("../../plots/baseline_NMR_pct_lean_18M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```


# NMR % Fat {.tabset}

## 6M Female

```{r}
plot_baseline(x = NMR, response = "pre_fat_pct",
              conf = filter(conf_df, response == "NMR % Fat"),
              stats = filter(BASELINE_STATS, response == "NMR % Fat"),
              sex = "Female", age = "6M") +
  labs(y  = "NMR % Fat Mass")

ggsave("../../plots/baseline_NMR_pct_fat_6M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```

## 6M Male

```{r}
plot_baseline(x = NMR, response = "pre_fat_pct",
              conf = filter(conf_df, response == "NMR % Fat"),
              stats = filter(BASELINE_STATS, response == "NMR % Fat"),
              sex = "Male", age = "6M") +
  labs(y  = "NMR % Fat Mass")

ggsave("../../plots/baseline_NMR_pct_fat_6M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```

## 18M Female

```{r}
plot_baseline(x = NMR, response = "pre_fat_pct",
              conf = filter(conf_df, response == "NMR % Fat"),
              stats = filter(BASELINE_STATS, response == "NMR % Fat"),
              sex = "Female", age = "18M") +
  labs(y  = "NMR % Fat Mass")

ggsave("../../plots/baseline_NMR_pct_fat_18M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```

## 18M Male

```{r}
plot_baseline(x = NMR, response = "pre_fat_pct",
              conf = filter(conf_df, response == "NMR % Fat"),
              stats = filter(BASELINE_STATS, response == "NMR % Fat"),
              sex = "Male", age = "18M") +
  labs(y  = "NMR % Fat Mass")

ggsave("../../plots/baseline_NMR_pct_fat_18M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```


# Absolute VO$_2$max {.tabset}

## 6M Female

```{r}
plot_baseline(x = VO2MAX, response = "pre_vo2max_ml_min",
              conf = filter(conf_df, response == "Absolute VO2max"),
              stats = filter(BASELINE_STATS, response == "Absolute VO2max"),
              sex = "Female", age = "6M") +
  labs(y  = TeX("VO$_2$max (mL/min)"))

ggsave("../../plots/baseline_absolute_VO2max_6M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```

## 6M Male

```{r}
plot_baseline(x = VO2MAX, response = "pre_vo2max_ml_min",
              conf = filter(conf_df, response == "Absolute VO2max"),
              stats = filter(BASELINE_STATS, response == "Absolute VO2max"),
              sex = "Male", age = "6M", y_position = 26) +
  labs(y  = TeX("VO$_2$max (mL/min)"))

ggsave("../../plots/baseline_absolute_VO2max_6M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```

## 18M Female

```{r, fig.width=1}
plot_baseline(x = VO2MAX, response = "pre_vo2max_ml_min",
              conf = filter(conf_df, response == "Absolute VO2max"),
              stats = filter(BASELINE_STATS, response == "Absolute VO2max"),
              sex = "Female", age = "18M") +
  labs(y  = TeX("VO$_2$max (mL/min)"))

ggsave("../../plots/baseline_absolute_VO2max_18M_female.png",
       height = 1.8, width = 1, dpi = 400)
```

## 18M Male

```{r, fig.width=1}
plot_baseline(x = VO2MAX, response = "pre_vo2max_ml_min",
              conf = filter(conf_df, response == "Absolute VO2max"),
              stats = filter(BASELINE_STATS, response == "Absolute VO2max"),
              sex = "Male", age = "18M") +
  labs(y  = TeX("VO$_2$max (mL/min)"))

ggsave("../../plots/baseline_absolute_VO2max_18M_male.png",
       height = 1.8, width = 1, dpi = 400)
```

# Relative VO$_2$max {.tabset}

## 6M Female

```{r}
plot_baseline(x = VO2MAX, response = "pre_vo2max_ml_kg_min",
              conf = filter(conf_df, response == "Relative VO2max"),
              stats = filter(BASELINE_STATS, response == "Relative VO2max"),
              sex = "Female", age = "6M") +
  labs(y  = TeX("VO$_2$max (mL/kg/min)"))

ggsave("../../plots/baseline_relative_VO2max_6M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```

## 6M Male

```{r}
plot_baseline(x = VO2MAX, response = "pre_vo2max_ml_kg_min",
              conf = filter(conf_df, response == "Relative VO2max"),
              stats = filter(BASELINE_STATS, response == "Relative VO2max"),
              sex = "Male", age = "6M") +
  labs(y  = TeX("VO$_2$max (mL/kg/min)"))

ggsave("../../plots/baseline_relative_VO2max_6M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```


## 18M Female

```{r, fig.width=1}
plot_baseline(x = VO2MAX, response = "pre_vo2max_ml_kg_min",
              conf = filter(conf_df, response == "Relative VO2max"),
              stats = filter(BASELINE_STATS, response == "Relative VO2max"),
              sex = "Female", age = "18M") +
  labs(y  = TeX("VO$_2$max (mL/kg/min)"))

ggsave("../../plots/baseline_relative_VO2max_18M_female.png",
       height = 1.8, width = 1, dpi = 400)
```

## 18M Male

```{r, fig.width=1}
plot_baseline(x = VO2MAX, response = "pre_vo2max_ml_kg_min",
              conf = filter(conf_df, response == "Relative VO2max"),
              stats = filter(BASELINE_STATS, response == "Relative VO2max"),
              sex = "Male", age = "18M") +
  labs(y  = TeX("VO$_2$max (mL/kg/min)"))

ggsave("../../plots/baseline_relative_VO2max_18M_male.png",
       height = 1.8, width = 1, dpi = 400)
```

# Maximum Run Speed {.tabset}

```{r}
# Custom theme for maximum run speed plots
t1 <- theme(text = element_text(size = 6.5, color = "black"),
            line = element_line(linewidth = 0.3, color = "black"),
            axis.ticks = element_line(linewidth = 0.3, color = "black"),
            panel.grid = element_blank(),
            panel.border = element_blank(),
            axis.ticks.x = element_blank(),
            axis.text = element_text(size = 5,
                                     color = "black"),
            axis.text.x = element_text(size = 6.5, angle = 90, hjust = 1,
                                       vjust = 0.5),
            axis.title = element_text(size = 6.5, margin = margin(),
                                      color = "black"),
            axis.line = element_line(linewidth = 0.3),
            strip.background = element_blank(),
            strip.text = element_blank(),
            panel.spacing = unit(-1, "pt"),
            plot.title = element_text(size = 7, color = "black"),
            plot.subtitle = element_text(size = 6, color = "black"),
            legend.position = "bottom",
            legend.direction = "horizontal",
            legend.title.align = 0.5,
            legend.key.size = unit(4, "pt"), 
            legend.box.spacing = unit(0, "pt"),
            legend.box.margin = margin(t = 0, b = 0, unit = "pt"),
            strip.placement = "outside"
)
```

## 6M Female

```{r}
VO2MAX %>% 
  filter(sex == "Female", age == "6M") %>% 
  count(age, sex, group, pre_speed_max) %>% 
  ggplot(aes(x = group, y = pre_speed_max, size = n)) +
  geom_point(shape = 16, color = "#ff6eff") +
  scale_size_area(max_size = 4, breaks = seq(2, 10, 4)) +
  scale_y_continuous(name = "Maximum Run Speed (m/min)",
                     breaks = seq(19.8, 36, 1.8),
                     limits = c(19.8, 28.8)) +
  labs(x = NULL) +
  theme_bw(base_size = 6) +
  t1

ggsave("../../plots/baseline_max_run_speed_6M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```


## 6M Male

```{r}
VO2MAX %>% 
  filter(sex == "Male", age == "6M") %>% 
  count(age, sex, group, pre_speed_max) %>% 
  ggplot(aes(x = group, y = pre_speed_max, size = n)) +
  geom_point(shape = 16, color = "#5555ff") +
  ggpubr::stat_pvalue_manual(
    data = data.frame(y.position = c(23.4, 25.2) + 0.5,
                      group1 = rep("SED", 2),
                      group2 = c("1W", "2W"),
                      label = c("         Wilcoxon p = 0.002", 
                                "   Wilcoxon p = 0.001")),
    label.size = 5 / .pt, vjust = -0.25
  ) +
  scale_size_area(max_size = 4, breaks = seq(2, 10, 4)) +
  scale_y_continuous(name = "Maximum Run Speed (m/min)",
                     breaks = seq(19.8, 25.2, 1.8)) +
  coord_cartesian(ylim = c(19.7, 25.2), clip = "off") +
  labs(x = NULL) +
  theme_bw(base_size = 6) +
  t1 +
  theme(plot.margin = unit(c(12, 5, 5, 5), units = "pt"))

ggsave("../../plots/baseline_max_run_speed_6M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```

## 18M Female

```{r, fig.width=1.2}
VO2MAX %>% 
  filter(sex == "Female", age == "18M") %>% 
  count(age, sex, group, pre_speed_max) %>% 
  ggplot(aes(x = group, y = pre_speed_max, size = n)) +
  geom_point(shape = 16, color = "#ff6eff") +
  scale_size_area(max_size = 4, breaks = seq(2, 10, 4)) +
  scale_y_continuous(name = "Maximum Run Speed (m/min)",
                     limits = c(16.2, 21.6),
                     breaks = seq(16.2, 21.6, 1.8)) +
  labs(x = NULL) +
  theme_bw(base_size = 6) +
  t1

ggsave("../../plots/baseline_max_run_speed_18M_female.png",
       height = 1.8, width = 1.2, dpi = 400)
```

## 18M Male

```{r, fig.width=1.2}
VO2MAX %>% 
  filter(sex == "Male", age == "18M") %>% 
  count(age, sex, group, pre_speed_max) %>% 
  ggplot(aes(x = group, y = pre_speed_max, size = n)) +
  geom_point(shape = 16, color = "#5555ff", na.rm = TRUE) +
  scale_size_area(max_size = 4, breaks = seq(2, 10, 4)) +
  scale_y_continuous(name = "Maximum Run Speed (m/min)",
                     limits = c(12.6, 18),
                     breaks = seq(12.6, 18, 1.8)) +
  labs(x = NULL) +
  theme_bw(base_size = 6) +
  t1

ggsave("../../plots/baseline_max_run_speed_18M_male.png",
       height = 1.8, width = 1.2, dpi = 400)
```
