---
title: "Plots of muscle measures"
output: 
  rmarkdown::html_document:
    code_folding: hide
    toc: true
    toc_depth: 2
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 1.5,
  fig.height = 1.8,
  out.height = "50%",
  out.width = "50%",
  dpi = 400,
  message = FALSE,
  warning = FALSE
)
```

```{r setup}
# Required packages
library(MotrpacRatTrainingPhysiologyData)
library(dplyr)
library(tibble)
library(tidyr)
library(purrr)
library(ggplot2)
library(latex2exp)
```

```{r}
# Reformat confidence interval data
conf_df <- map(MUSCLES_EMM, function(emm_i) {
  terms_i <- attr(terms(emm_i@model.info), which = "term.labels")
  
  out <- summary(emm_i) %>% 
    as.data.frame() %>% 
    rename(any_of(c(lower.CL = "asymp.LCL",
                    upper.CL = "asymp.UCL",
                    response_mean = "response",
                    response_mean = "rate")))
  
  if ("age_group" %in% terms_i) {
    out <- mutate(out,
                  age = sub("_.*", "", age_group),
                  group = sub(".*_", "", age_group),
                  age_group = NULL)
  }
  
  out <- out %>% 
    mutate(group = factor(group, 
                          levels = c("SED", paste0(2 ^ (0:3), "W"))))
  
  return(out)
}) %>% 
  enframe(name = "response") %>% 
  unnest(value)
```

# Glycogen

## LG {.tabset}

### 6M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "LG"), 
              response = "glycogen",
              conf = filter(conf_df, response == "Glycogen", 
                            muscle == "LG"),
              stats = filter(MUSCLES_STATS, response == "Glycogen", 
                             muscle == "LG"),
              sex = "Female", age = "6M", y_position = 3.9) +
  scale_y_continuous(name  = TeX("LG Glycogen (ng/$\\mu$L/mg)"),
                     breaks = seq(0, 4, 1),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 4.5), clip = "off") +
  theme(plot.margin = unit(c(12, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_glycogen_LG_6M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```

### 6M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "LG"), 
              response = "glycogen",
              conf = filter(conf_df, response == "Glycogen", 
                            muscle == "LG"),
              stats = filter(MUSCLES_STATS, response == "Glycogen", 
                             muscle == "LG"),
              sex = "Male", age = "6M", y_position = 9.5) +
  scale_y_continuous(name  = TeX("LG Glycogen (ng/$\\mu$L/mg)"),
                     breaks = seq(0, 10, 2),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 10), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_glycogen_LG_6M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```

### 18M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "LG"), 
              response = "glycogen",
              conf = filter(conf_df, response == "Glycogen", 
                            muscle == "LG"),
              stats = filter(MUSCLES_STATS, response == "Glycogen", 
                             muscle == "LG"),
              sex = "Female", age = "18M") +
  scale_y_continuous(name  = TeX("LG Glycogen (ng/$\\mu$L/mg)"),
                     breaks = seq(0, 10, 2),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 11), clip = "off") +
  theme(plot.margin = unit(c(12, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_glycogen_LG_18M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```


### 18M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "LG"), 
              response = "glycogen",
              conf = filter(conf_df, response == "Glycogen", 
                            muscle == "LG"),
              stats = filter(MUSCLES_STATS, response == "Glycogen", 
                             muscle == "LG"),
              sex = "Male", age = "18M", y_position = 15.5) +
  scale_y_continuous(name  = TeX("LG Glycogen (ng/$\\mu$L/mg)"),
                     breaks = seq(0, 16, 4),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 16), clip = "off") +
  theme(plot.margin = unit(c(15, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_glycogen_LG_18M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```


## MG {.tabset}

### 6M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "MG"), 
              response = "glycogen",
              conf = filter(conf_df, response == "Glycogen", 
                            muscle == "MG"),
              stats = filter(MUSCLES_STATS, response == "Glycogen", 
                             muscle == "MG"),
              sex = "Female", age = "6M") +
  scale_y_continuous(name  = TeX("MG Glycogen (ng/$\\mu$L/mg)"),
                     breaks = seq(0, 10, 2),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 11), clip = "off") +
  theme(plot.margin = unit(c(12, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_glycogen_MG_6M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```

### 6M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "MG"), 
              response = "glycogen",
              conf = filter(conf_df, response == "Glycogen", 
                            muscle == "MG"),
              stats = filter(MUSCLES_STATS, response == "Glycogen", 
                             muscle == "MG"),
              sex = "Male", age = "6M") +
  scale_y_continuous(name  = TeX("MG Glycogen (ng/$\\mu$L/mg)"),
                     breaks = seq(0, 16, 4),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 16), clip = "off") +
  theme(plot.margin = unit(c(12, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_glycogen_MG_6M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```

### 18M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "MG"), 
              response = "glycogen",
              conf = filter(conf_df, response == "Glycogen", 
                            muscle == "MG"),
              stats = filter(MUSCLES_STATS, response == "Glycogen", 
                             muscle == "MG"),
              sex = "Female", age = "18M") +
  scale_y_continuous(name  = TeX("MG Glycogen (ng/$\\mu$L/mg)"),
                     breaks = seq(0, 12, 4),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 13), clip = "off") +
  theme(plot.margin = unit(c(12, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_glycogen_MG_18M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```


### 18M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "MG"), 
              response = "glycogen",
              conf = filter(conf_df, response == "Glycogen", 
                            muscle == "MG"),
              stats = filter(MUSCLES_STATS, response == "Glycogen", 
                             muscle == "MG"),
              sex = "Male", age = "18M") +
  scale_y_continuous(name  = TeX("MG Glycogen (ng/$\\mu$L/mg)"),
                     breaks = seq(0, 20, 5),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 20), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_glycogen_MG_18M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```


## PL {.tabset}

### 6M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "PL"), 
              response = "glycogen",
              conf = filter(conf_df, response == "Glycogen", 
                            muscle == "PL"),
              stats = filter(MUSCLES_STATS, response == "Glycogen", 
                             muscle == "PL"),
              sex = "Female", age = "6M", y_position = 11.4) +
  scale_y_continuous(name  = TeX("PL Glycogen (ng/$\\mu$L/mg)"),
                     breaks = seq(0, 12, 4),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 12), clip = "off") +
  theme(plot.margin = unit(c(12, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_glycogen_PL_6M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```

### 6M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "PL"), 
              response = "glycogen",
              conf = filter(conf_df, response == "Glycogen", 
                            muscle == "PL"),
              stats = filter(MUSCLES_STATS, response == "Glycogen", 
                             muscle == "PL"),
              sex = "Male", age = "6M", y_position = 13) +
  scale_y_continuous(name  = TeX("PL Glycogen (ng/$\\mu$L/mg)"),
                     breaks = seq(0, 15, 5),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 15), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_glycogen_PL_6M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```

### 18M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "PL"), 
              response = "glycogen",
              conf = filter(conf_df, response == "Glycogen", 
                            muscle == "PL"),
              stats = filter(MUSCLES_STATS, response == "Glycogen", 
                             muscle == "PL"),
              sex = "Female", age = "18M") +
  scale_y_continuous(name  = TeX("PL Glycogen (ng/$\\mu$L/mg)"),
                     breaks = seq(0, 30, 10),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 30), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_glycogen_PL_18M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```

### 18M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "PL"), 
              response = "glycogen",
              conf = filter(conf_df, response == "Glycogen", 
                            muscle == "PL"),
              stats = filter(MUSCLES_STATS, response == "Glycogen", 
                             muscle == "PL"),
              sex = "Male", age = "18M") +
  scale_y_continuous(name  = TeX("PL Glycogen (ng/$\\mu$L/mg)"),
                     breaks = seq(0, 25, 5),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 25), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_glycogen_PL_18M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```


## SOL {.tabset}

### 6M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "SOL"), 
              response = "glycogen",
              conf = filter(conf_df, response == "Glycogen", 
                            muscle == "SOL"),
              stats = filter(MUSCLES_STATS, response == "Glycogen", 
                             muscle == "SOL"),
              sex = "Female", age = "6M") +
  scale_y_continuous(name  = TeX("SOL Glycogen (ng/$\\mu$L/mg)"),
                     breaks = seq(5, 25, 5),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(5, 25), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_glycogen_SOL_6M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```

### 6M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "SOL"), 
              response = "glycogen",
              conf = filter(conf_df, response == "Glycogen", 
                            muscle == "SOL"),
              stats = filter(MUSCLES_STATS, response == "Glycogen", 
                             muscle == "SOL"),
              sex = "Male", age = "6M", y_position = 27) +
  scale_y_continuous(name  = TeX("SOL Glycogen (ng/$\\mu$L/mg)"),
                     breaks = seq(0, 30, 10),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 30), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_glycogen_SOL_6M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```

### 18M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "SOL"), 
              response = "glycogen",
              conf = filter(conf_df, response == "Glycogen", 
                            muscle == "SOL"),
              stats = filter(MUSCLES_STATS, response == "Glycogen", 
                             muscle == "SOL"),
              sex = "Female", age = "18M", y_position = 50) +
  scale_y_continuous(name  = TeX("SOL Glycogen (ng/$\\mu$L/mg)"),
                     breaks = seq(0, 60, 20),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 64), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_glycogen_SOL_18M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```

### 18M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "SOL"), 
              response = "glycogen",
              conf = filter(conf_df, response == "Glycogen", 
                            muscle == "SOL"),
              stats = filter(MUSCLES_STATS, response == "Glycogen", 
                             muscle == "SOL"),
              sex = "Male", age = "18M") +
  scale_y_continuous(name  = TeX("SOL Glycogen (ng/$\\mu$L/mg)"),
                     breaks = seq(10, 35, 5),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(9, 35), clip = "off") +
  theme(plot.margin = unit(c(8, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_glycogen_SOL_18M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```


# Citrate Synthase

## LG {.tabset}

### 6M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "LG"), 
              response = "citrate_synthase",
              conf = filter(conf_df, response == "Citrate Synthase", 
                            muscle == "LG"),
              stats = filter(MUSCLES_STATS, response == "Citrate Synthase", 
                             muscle == "LG"),
              sex = "Female", age = "6M", y_position = 300) +
  scale_y_continuous(name  = TeX("LG CS (U/$\\mu$g protein $\\times 10^3$)"),
                     breaks = seq(0, 350, 100),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 350), clip = "off") +
  theme(plot.margin = unit(c(16, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_citrate_synthase_LG_6M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```


### 6M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "LG"), 
              response = "citrate_synthase",
              conf = filter(conf_df, response == "Citrate Synthase", 
                            muscle == "LG"),
              stats = filter(MUSCLES_STATS, response == "Citrate Synthase", 
                             muscle == "LG"),
              sex = "Male", age = "6M", y_position = 460) +
  scale_y_continuous(name  = TeX("LG CS (U/$\\mu$g protein $\\times 10^3$)"),
                     breaks = seq(0, 500, 100),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 530), clip = "off") +
  theme(plot.margin = unit(c(10, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_citrate_synthase_LG_6M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```

### 18M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "LG"), 
              response = "citrate_synthase",
              conf = filter(conf_df, response == "Citrate Synthase", 
                            muscle == "LG"),
              stats = filter(MUSCLES_STATS, response == "Citrate Synthase", 
                             muscle == "LG"),
              sex = "Female", age = "18M", y_position = 260) +
  scale_y_continuous(name  = TeX("LG CS (U/$\\mu$g protein $\\times 10^3$)"),
                     breaks = seq(0, 300, 100),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 350), clip = "off") +
  theme(plot.margin = unit(c(12, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_citrate_synthase_LG_18M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```


### 18M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "LG"), 
              response = "citrate_synthase",
              conf = filter(conf_df, response == "Citrate Synthase", 
                            muscle == "LG"),
              stats = filter(MUSCLES_STATS, response == "Citrate Synthase", 
                             muscle == "LG"),
              sex = "Male", age = "18M") +
  scale_y_continuous(name  = TeX("LG CS (U/$\\mu$g protein $\\times 10^3$)"),
                     breaks = seq(0, 500, 100),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 500), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_citrate_synthase_LG_18M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```


## MG {.tabset}

### 6M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "MG"), 
              response = "citrate_synthase",
              conf = filter(conf_df, response == "Citrate Synthase", 
                            muscle == "MG"),
              stats = filter(MUSCLES_STATS, response == "Citrate Synthase", 
                             muscle == "MG"),
              sex = "Female", age = "6M", y_position = 270) +
  scale_y_continuous(name  = TeX("MG CS (U/$\\mu$g protein $\\times 10^3$)"),
                     breaks = seq(0, 300, 100),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 310), clip = "off") +
  theme(plot.margin = unit(c(16, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_citrate_synthase_MG_6M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```


### 6M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "MG"), 
              response = "citrate_synthase",
              conf = filter(conf_df, response == "Citrate Synthase", 
                            muscle == "MG"),
              stats = filter(MUSCLES_STATS, response == "Citrate Synthase", 
                             muscle == "MG"),
              sex = "Male", age = "6M", y_position = 450) +
  scale_y_continuous(name  = TeX("MG CS (U/$\\mu$g protein $\\times 10^3$)"),
                     breaks = seq(0, 500, 100),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 500), clip = "off") +
  theme(plot.margin = unit(c(15, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_citrate_synthase_MG_6M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```

### 18M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "MG"), 
              response = "citrate_synthase",
              conf = filter(conf_df, response == "Citrate Synthase", 
                            muscle == "MG"),
              stats = filter(MUSCLES_STATS, response == "Citrate Synthase", 
                             muscle == "MG"),
              sex = "Female", age = "18M", y_position = 240) +
  scale_y_continuous(name  = TeX("MG CS (U/$\\mu$g protein $\\times 10^3$)"),
                     breaks = seq(0, 300, 100),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 300), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_citrate_synthase_MG_18M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```


### 18M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "MG"), 
              response = "citrate_synthase",
              conf = filter(conf_df, response == "Citrate Synthase", 
                            muscle == "MG"),
              stats = filter(MUSCLES_STATS, response == "Citrate Synthase", 
                             muscle == "MG"),
              sex = "Male", age = "18M") +
  scale_y_continuous(name  = TeX("MG CS (U/$\\mu$g protein $\\times 10^3$)"),
                     breaks = seq(0, 400, 100),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 400), clip = "off") +
  theme(plot.margin = unit(c(8, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_citrate_synthase_MG_18M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```


## PL {.tabset}

### 6M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "PL"), 
              response = "citrate_synthase",
              conf = filter(conf_df, response == "Citrate Synthase", 
                            muscle == "PL"),
              stats = filter(MUSCLES_STATS, response == "Citrate Synthase", 
                             muscle == "PL"),
              sex = "Female", age = "6M", y_position = 210) +
  scale_y_continuous(name  = TeX("PL CS (U/$\\mu$g protein $\\times 10^3$)"),
                     breaks = seq(0, 250, 50),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 250), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_citrate_synthase_PL_6M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```


### 6M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "PL"), 
              response = "citrate_synthase",
              conf = filter(conf_df, response == "Citrate Synthase", 
                            muscle == "PL"),
              stats = filter(MUSCLES_STATS, response == "Citrate Synthase", 
                             muscle == "PL"),
              sex = "Male", age = "6M", y_position = 320) +
  scale_y_continuous(name  = TeX("PL CS (U/$\\mu$g protein $\\times 10^3$)"),
                     breaks = seq(0, 400, 100),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 400), clip = "off") +
  theme(plot.margin = unit(c(10, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_citrate_synthase_PL_6M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```

### 18M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "PL"), 
              response = "citrate_synthase",
              conf = filter(conf_df, response == "Citrate Synthase", 
                            muscle == "PL"),
              stats = filter(MUSCLES_STATS, response == "Citrate Synthase", 
                             muscle == "PL"),
              sex = "Female", age = "18M", y_position = 194) +
  scale_y_continuous(name  = TeX("PL CS (U/$\\mu$g protein $\\times 10^3$)"),
                     breaks = seq(0, 200, 50),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 210), clip = "off") +
  theme(plot.margin = unit(c(10, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_citrate_synthase_PL_18M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```


### 18M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "PL"), 
              response = "citrate_synthase",
              conf = filter(conf_df, response == "Citrate Synthase", 
                            muscle == "PL"),
              stats = filter(MUSCLES_STATS, response == "Citrate Synthase", 
                             muscle == "PL"),
              sex = "Male", age = "18M") +
  scale_y_continuous(name  = TeX("PL CS (U/$\\mu$g protein $\\times 10^3$)"),
                     breaks = seq(0, 400, 100),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 400), clip = "off") +
  theme(plot.margin = unit(c(10, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_citrate_synthase_PL_18M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```


## SOL {.tabset}

### 6M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "SOL"), 
              response = "citrate_synthase",
              conf = filter(conf_df, response == "Citrate Synthase", 
                            muscle == "SOL"),
              stats = filter(MUSCLES_STATS, response == "Citrate Synthase", 
                             muscle == "SOL"),
              sex = "Female", age = "6M", y_position = 310) +
  scale_y_continuous(name  = TeX("SOL CS (U/$\\mu$g protein $\\times 10^3$)"),
                     breaks = seq(0, 300, 100),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 320), clip = "off") +
  theme(plot.margin = unit(c(25, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_citrate_synthase_SOL_6M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```


### 6M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "SOL"), 
              response = "citrate_synthase",
              conf = filter(conf_df, response == "Citrate Synthase", 
                            muscle == "SOL"),
              stats = filter(MUSCLES_STATS, response == "Citrate Synthase", 
                             muscle == "SOL"),
              sex = "Male", age = "6M", y_position = 450) +
  scale_y_continuous(name  = TeX("SOL CS (U/$\\mu$g protein $\\times 10^3$)"),
                     breaks = seq(0, 500, 100),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 500), clip = "off") +
  theme(plot.margin = unit(c(18, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_citrate_synthase_SOL_6M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```

### 18M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "SOL"), 
              response = "citrate_synthase",
              conf = filter(conf_df, response == "Citrate Synthase", 
                            muscle == "SOL"),
              stats = filter(MUSCLES_STATS, response == "Citrate Synthase", 
                             muscle == "SOL"),
              sex = "Female", age = "18M", y_position = 230) +
  scale_y_continuous(name  = TeX("SOL CS (U/$\\mu$g protein $\\times 10^3$)"),
                     breaks = seq(0, 250, 50),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 250), clip = "off") +
  theme(plot.margin = unit(c(8, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_citrate_synthase_SOL_18M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```


### 18M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "SOL"), 
              response = "citrate_synthase",
              conf = filter(conf_df, response == "Citrate Synthase", 
                            muscle == "SOL"),
              stats = filter(MUSCLES_STATS, response == "Citrate Synthase", 
                             muscle == "SOL"),
              sex = "Male", age = "18M") +
  scale_y_continuous(name  = TeX("SOL CS (U/$\\mu$g protein $\\times 10^3$)"),
                     breaks = seq(0, 300, 100),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(0, 300), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_citrate_synthase_SOL_18M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```




# Terminal Mass

## LG {.tabset}

### 6M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "LG"), 
              response = "term_weight",
              conf = filter(conf_df, response == "Terminal Weight", 
                            muscle == "LG"),
              stats = filter(MUSCLES_STATS, response == "Terminal Weight", 
                             muscle == "LG"),
              sex = "Female", age = "6M", y_position = 620) +
  scale_y_continuous(name  = "LG Terminal Mass (g)",
                     breaks = seq(500, 700, 100),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(485, 700), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_term_weight_LG_6M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```


### 6M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "LG"), 
              response = "term_weight",
              conf = filter(conf_df, response == "Terminal Weight", 
                            muscle == "LG"),
              stats = filter(MUSCLES_STATS, response == "Terminal Weight", 
                             muscle == "LG"),
              sex = "Male", age = "6M") +
  scale_y_continuous(name  = "LG Terminal Mass (g)",
                     breaks = seq(700, 1000, 100),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(650, 1060), clip = "off") +
  theme(plot.margin = unit(c(8, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_term_weight_LG_6M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```

### 18M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "LG"), 
              response = "term_weight",
              conf = filter(conf_df, response == "Terminal Weight", 
                            muscle == "LG"),
              stats = filter(MUSCLES_STATS, response == "Terminal Weight", 
                             muscle == "LG"),
              sex = "Female", age = "18M") +
  scale_y_continuous(name  = "LG Terminal Mass (g)",
                     breaks = seq(500, 620, 40),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(490, 625), clip = "off") +
  theme(plot.margin = unit(c(12, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_term_weight_LG_18M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```


### 18M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "LG"), 
              response = "term_weight",
              conf = filter(conf_df, response == "Terminal Weight", 
                            muscle == "LG"),
              stats = filter(MUSCLES_STATS, response == "Terminal Weight", 
                             muscle == "LG"),
              sex = "Male", age = "18M", y_position = 940) +
  scale_y_continuous(name  = "LG Terminal Mass (g)",
                     breaks = seq(750, 1000, 50),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(750, 1000), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_term_weight_LG_18M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```


## MG {.tabset}

### 6M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "MG"), 
              response = "term_weight",
              conf = filter(conf_df, response == "Terminal Weight", 
                            muscle == "MG"),
              stats = filter(MUSCLES_STATS, response == "Terminal Weight", 
                             muscle == "MG"),
              sex = "Female", age = "6M") +
  scale_y_continuous(name  = "MG Terminal Mass (g)",
                     breaks = seq(320, 450, 20),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(315, 450), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_term_weight_MG_6M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```


### 6M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "MG"), 
              response = "term_weight",
              conf = filter(conf_df, response == "Terminal Weight", 
                            muscle == "MG"),
              stats = filter(MUSCLES_STATS, response == "Terminal Weight", 
                             muscle == "MG"),
              sex = "Male", age = "6M") +
  scale_y_continuous(name  = "MG Terminal Mass (g)",
                     breaks = seq(500, 750, 50),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(500, 770), clip = "off") +
  theme(plot.margin = unit(c(10, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_term_weight_MG_6M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```

### 18M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "MG"), 
              response = "term_weight",
              conf = filter(conf_df, response == "Terminal Weight", 
                            muscle == "MG"),
              stats = filter(MUSCLES_STATS, response == "Terminal Weight", 
                             muscle == "MG"),
              sex = "Female", age = "18M") +
  scale_y_continuous(name  = "MG Terminal Mass (g)",
                     breaks = seq(350, 470, 20),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(350, 472), clip = "off") +
  theme(plot.margin = unit(c(10, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_term_weight_MG_18M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```


### 18M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "MG"), 
              response = "term_weight",
              conf = filter(conf_df, response == "Terminal Weight", 
                            muscle == "MG"),
              stats = filter(MUSCLES_STATS, response == "Terminal Weight", 
                             muscle == "MG"),
              sex = "Male", age = "18M") +
  scale_y_continuous(name  = "MG Terminal Mass (g)",
                     breaks = seq(550, 750, 50),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(550, 750), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_term_weight_MG_18M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```


## PL {.tabset}

### 6M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "PL"), 
              response = "term_weight",
              conf = filter(conf_df, response == "Terminal Weight", 
                            muscle == "PL"),
              stats = filter(MUSCLES_STATS, response == "Terminal Weight", 
                             muscle == "PL"),
              sex = "Female", age = "6M", y_position = 212) +
  scale_y_continuous(name  = "PL Terminal Mass (g)",
                     breaks = seq(160, 220, 20),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(160, 220), clip = "off") +
  theme(plot.margin = unit(c(16, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_term_weight_PL_6M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```


### 6M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "PL"), 
              response = "term_weight",
              conf = filter(conf_df, response == "Terminal Weight", 
                            muscle == "PL"),
              stats = filter(MUSCLES_STATS, response == "Terminal Weight", 
                             muscle == "PL"),
              sex = "Male", age = "6M") +
  scale_y_continuous(name  = "PL Terminal Mass (g)",
                     breaks = seq(250, 370, 40),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(245, 375), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_term_weight_PL_6M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```

### 18M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "PL"), 
              response = "term_weight",
              conf = filter(conf_df, response == "Terminal Weight", 
                            muscle == "PL"),
              stats = filter(MUSCLES_STATS, response == "Terminal Weight", 
                             muscle == "PL"),
              sex = "Female", age = "18M") +
  scale_y_continuous(name  = "PL Terminal Mass (g)",
                     breaks = seq(160, 220, 20),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(160, 225), clip = "off") +
  theme(plot.margin = unit(c(8, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_term_weight_PL_18M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```


### 18M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "PL"), 
              response = "term_weight",
              conf = filter(conf_df, response == "Terminal Weight", 
                            muscle == "PL"),
              stats = filter(MUSCLES_STATS, response == "Terminal Weight", 
                             muscle == "PL"),
              sex = "Male", age = "18M") +
  scale_y_continuous(name  = "PL Terminal Mass (g)",
                     breaks = seq(200, 380, 40),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(200, 380), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_term_weight_PL_18M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```


## SOL {.tabset}

### 6M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "SOL"), 
              response = "term_weight",
              conf = filter(conf_df, response == "Terminal Weight", 
                            muscle == "SOL"),
              stats = filter(MUSCLES_STATS, response == "Terminal Weight", 
                             muscle == "SOL"),
              sex = "Female", age = "6M", y_position = 101) +
  scale_y_continuous(name  = "SOL Terminal Mass (g)",
                     breaks = seq(60, 110, 10),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(60, 110), clip = "off") +
  theme(plot.margin = unit(c(8, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_term_weight_SOL_6M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```


### 6M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "SOL"), 
              response = "term_weight",
              conf = filter(conf_df, response == "Terminal Weight", 
                            muscle == "SOL"),
              stats = filter(MUSCLES_STATS, response == "Terminal Weight", 
                             muscle == "SOL"),
              sex = "Male", age = "6M") +
  scale_y_continuous(name  = "SOL Terminal Mass (g)",
                     breaks = seq(100, 180, 20),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(100, 180), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_term_weight_SOL_6M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```

### 18M Female

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "SOL"), 
              response = "term_weight",
              conf = filter(conf_df, response == "Terminal Weight", 
                            muscle == "SOL"),
              stats = filter(MUSCLES_STATS, response == "Terminal Weight", 
                             muscle == "SOL"),
              sex = "Female", age = "18M") +
  scale_y_continuous(name  = "SOL Terminal Mass (g)",
                     breaks = seq(70, 100, 10),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(65, 103), clip = "off") +
  theme(plot.margin = unit(c(10, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_term_weight_SOL_18M_female.png",
       height = 1.8, width = 1.5, dpi = 400)
```


### 18M Male

```{r}
plot_baseline(x = filter(MUSCLES, muscle == "SOL"), 
              response = "term_weight",
              conf = filter(conf_df, response == "Terminal Weight", 
                            muscle == "SOL"),
              stats = filter(MUSCLES_STATS, response == "Terminal Weight", 
                             muscle == "SOL"),
              sex = "Male", age = "18M") +
  scale_y_continuous(name  = "SOL Terminal Mass (g)",
                     breaks = seq(80, 180, 20),
                     expand = expansion(mult = 1e-2)) +
  coord_cartesian(ylim = c(70, 180), clip = "off") +
  theme(plot.margin = unit(c(5, 5, 5, 5), units = "pt"))

ggsave("../../plots/muscle_term_weight_SOL_18M_male.png",
       height = 1.8, width = 1.5, dpi = 400)
```



# Mean CSA

```{r}
# Reformat confidence interval data
conf_df <- map(MUSCLES_EMM, function(emm_i) {
  terms_i <- attr(terms(emm_i@model.info), which = "term.labels")
  
  out <- summary(emm_i) %>% 
    as.data.frame() %>% 
    rename(any_of(c(lower.CL = "asymp.LCL",
                    upper.CL = "asymp.UCL",
                    response_mean = "response",
                    response_mean = "rate")))
  
  if ("age_group" %in% terms_i) {
    out <- mutate(out,
                  age = sub("_.*", "", age_group),
                  group = sub(".*_", "", age_group),
                  age_group = NULL)
  }
  
  out <- out %>% 
    mutate(group = factor(group, 
                          levels = c("SED", paste0(2 ^ (0:3), "W"))))
  
  return(out)
}) %>% 
  enframe(name = "response") %>% 
  unnest(value)
```


```{r}
f1 <- function(response, sex, age, 
               conf_df, stats_df,
               bracket.nudge.y = 0) {
  
  x <- MUSCLES %>% 
    dplyr::rename(response = !!sym(response)) %>% 
    filter(!is.na(response)) %>% 
    droplevels.data.frame() %>% 
    filter(age == !!age, sex == !!sex)
  
  conf_df <- filter(conf_df, age == !!age, sex == !!sex)
  
  y_pos <- x %>% 
    group_by(muscle) %>% 
    summarise(y.position = max(response))
  
  stats_df <- stats_df %>% # response == "Mean CSA"
    filter(signif != "") %>% 
    filter(age == !!age, sex == !!sex) %>% 
    mutate(contrast = as.character(contrast),
           group1 = sub(" .*", "", contrast),
           group2 = sub(".* ", "", contrast)) %>% 
    left_join(y_pos, by = "muscle")
  
  p <- ggplot(x, aes(x = group, y = response)) +
    geom_crossbar(data = conf_df,
                  aes(x = group, y = response_mean, 
                      ymin = lower.CL, ymax = upper.CL,
                      color = sex),
                  fatten = 1, linewidth = 0.5, width = 0.7) +
    geom_point(shape = 16, size = 0.5,
               position = ggbeeswarm::position_beeswarm(cex = 6, 
                                                        dodge.width = 0.7)) +
    ggpubr::stat_pvalue_manual(data = stats_df, 
                               label = "signif", 
                               size = 3.5, 
                               bracket.nudge.y = bracket.nudge.y) +
    annotation_custom(grob = linesGrob(x = c(0, 1), 
                                       y = unit(-20, "pt"),
                                       gp = gpar(lwd = 0.9)), 
                      xmin = -Inf, xmax = Inf, 
                      ymin = -Inf, ymax = Inf) +
    facet_grid(~ muscle, switch = "x") +
    scale_color_manual(values = c("#ff6eff", "#5555ff"),
                       breaks = c("Female", "Male")) +
    labs(x = NULL) +
    theme_bw() +
    theme(text = element_text(size = 6.5, color = "black"),
          line = element_line(linewidth = 0.3, color = "black"),
          axis.ticks = element_line(linewidth = 0.3, color = "black"),
          panel.grid = element_blank(),
          panel.border = element_blank(),
          axis.ticks.x = element_blank(),
          axis.text = element_text(size = 5,
                                   color = "black"),
          axis.text.x = element_text(size = 6.5, angle = 90, hjust = 1,
                                     vjust = 0.5),
          axis.title = element_text(size = 6.5, margin = margin(),
                                    color = "black"),
          axis.line = element_line(color = "black", linewidth = 0.3),
          strip.background = element_blank(),
          strip.text = element_text(size = 7, color = "black", 
                                    margin = margin(b = 0, t = 2)),
          panel.spacing = unit(2, "pt"),
          plot.title = element_text(size = 7, color = "black"),
          plot.subtitle = element_text(size = 6, color = "black"),
          legend.position = "none",
          strip.placement = "outside"
    )
  
  return(p)
}
```

```{r}
f1(response = "mean_CSA", sex = "Female", age = "6M", 
   conf_df = filter(conf_df, response == "Mean CSA"), 
   stats_df = filter(MUSCLES_STATS, response == "Mean CSA"), 
   bracket.nudge.y = 70) +
  scale_y_continuous(name = TeX("Mean CSA ($\\mu m^2$)"),
                     breaks = seq(1000, 2500, 500),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(1000, 2500), clip = "off")

ggsave("../../plots/mean_CSA_6M_female.png", 
       height = 1.7, width = 2, dpi = 400)
```


```{r}
f1(response = "mean_CSA", sex = "Male", age = "6M", 
   conf_df = filter(conf_df, response == "Mean CSA"), 
   stats_df = filter(MUSCLES_STATS, response == "Mean CSA")) +
  scale_y_continuous(name = TeX("Mean CSA ($\\mu m^2$)"),
                     breaks = seq(1500, 3500, 500),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(1500, 3500), clip = "off")

ggsave("../../plots/mean_CSA_6M_male.png", 
       height = 1.7, width = 2, dpi = 400)
```


```{r}
f1(response = "mean_CSA", sex = "Female", age = "18M", 
   conf_df = filter(conf_df, response == "Mean CSA"), 
   stats_df = filter(MUSCLES_STATS, response == "Mean CSA")) +
  scale_y_continuous(name = TeX("Mean CSA ($\\mu m^2$)"),
                     breaks = seq(1500, 2500, 500),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(1370, 2500), clip = "off")

ggsave("../../plots/mean_CSA_18M_female.png", 
       height = 1.7, width = 2, dpi = 400)
```


```{r}
f1(response = "mean_CSA", sex = "Male", age = "18M", 
   conf_df = filter(conf_df, response == "Mean CSA"), 
   stats_df = filter(MUSCLES_STATS, response == "Mean CSA"), 
   bracket.nudge.y = 70) +
  scale_y_continuous(name = TeX("Mean CSA ($\\mu m^2$)"),
                     breaks = seq(1600, 2800, 400),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(1600, 2800), clip = "off") +
  theme(plot.margin = margin(t = 10))

ggsave("../../plots/mean_CSA_18M_male.png", 
       height = 1.7, width = 2, dpi = 400)
```


# Capillary Contacts

```{r}
f1(response = "capillary_contacts", sex = "Female", age = "6M", 
   conf_df = filter(conf_df, response == "Capillary Contacts"), 
   stats_df = filter(MUSCLES_STATS, response == "Capillary Contacts")) +
  scale_y_continuous(name = "Capillary Contacts (#/capillary)",
                     breaks = seq(3, 5, 0.5),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(3, 5), clip = "off")

ggsave("../../plots/capillary_contacts_6M_female.png", 
       height = 1.7, width = 2, dpi = 400)
```


```{r}
f1(response = "capillary_contacts", sex = "Male", age = "6M", 
   conf_df = filter(conf_df, response == "Capillary Contacts"), 
   stats_df = filter(MUSCLES_STATS, response == "Capillary Contacts")) +
  scale_y_continuous(name = "Capillary Contacts (#/capillary)",
                     breaks = seq(3, 5.5, 0.5),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(2.95, 5.5), clip = "off")

ggsave("../../plots/capillary_contacts_6M_male.png", 
       height = 1.7, width = 2, dpi = 400)
```


```{r}
f1(response = "capillary_contacts", sex = "Female", age = "18M", 
   conf_df = filter(conf_df, response == "Capillary Contacts"), 
   stats_df = filter(MUSCLES_STATS, response == "Capillary Contacts")) +
  scale_y_continuous(name = "Capillary Contacts (#/capillary)",
                     breaks = seq(3, 4.5, 0.5),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(3, 4.5), clip = "off")

ggsave("../../plots/capillary_contacts_18M_female.png", 
       height = 1.7, width = 2, dpi = 400)
```


```{r}
f1(response = "capillary_contacts", sex = "Male", age = "18M", 
   conf_df = filter(conf_df, response == "Capillary Contacts"), 
   stats_df = filter(MUSCLES_STATS, response == "Capillary Contacts")) +
  scale_y_continuous(name = "Capillary Contacts (#/capillary)",
                     breaks = seq(3.5, 5.5, 0.5),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(3.5, 5.5), clip = "off")

ggsave("../../plots/capillary_contacts_18M_male.png", 
       height = 1.7, width = 2, dpi = 400)
```
