---
title: "Plots of post- vs. pre-training body composition and VO2max testing measures"
author: Tyler Sagendorf
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  rmarkdown::html_document:
    code_folding: hide
    toc: true
    toc_depth: 2
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 1.8,
  fig.height = 1.6,
  out.height = "50%",
  out.width = "50%",
  dpi = 400,
  message = FALSE,
  warning = FALSE
)

save_plots <- dir.exists(paths = file.path("..", "..", "plots"))
```

```{r setup}
# Required packages
library(MotrpacRatTrainingPhysiologyData)
library(dplyr)
library(ggplot2)
library(latex2exp)
```


# Overview

This article generates all plots of pre- and post-training NMR body composition and VO$_2$max testing measures: body mass recorded on the NMR day, NMR lean mass, NMR fat mass, NMR % lean mass, NMR % fat mass, absolute VO$_2$max, relative VO$_2$max, and maximum run speed. The line segments span from the pre to post value of each sample, with red indicating an increase, blue indicating a decrease, and a black point indicating no change. An asterisk indicates the mean of the (post - pre) differences is significantly different from zero (Holm-adjusted p-value < 0.05), and the direction of change is determined by the majority color (red or blue) of the line segments. Please refer to the "Statistical analyses of post- vs. pre-training body composition and VO2max testing measures" vignette for code to generate `PRE_POST_STATS`.


# NMR Body Mass

Body mass (g) recorded on the same day as the NMR body composition measures.

## 6M Female

```{r}
# 6M Female NMR Body Mass
plot_pre_post(x = filter(NMR, age == "6M", sex == "Female"), 
              pre = "pre_body_mass", post = "post_body_mass", 
              stats = filter(PRE_POST_STATS, response == "NMR Body Mass", 
                             age == "6M", sex == "Female")) +
  scale_y_continuous(name = "Body Mass (g)",
                     breaks = seq(160, 280, 20),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(155, 280), clip = "off") +
  geom_vline(xintercept = c(1.5, 2.5), color = "grey90", lwd = 0.3)
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "NMR_body_mass_6M_female.pdf"), 
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 6M Male

```{r}
# 6M Male NMR Body Mass
plot_pre_post(x = filter(NMR, age == "6M", sex == "Male"), 
              pre = "pre_body_mass", post = "post_body_mass", 
              stats = filter(PRE_POST_STATS, response == "NMR Body Mass", 
                             age == "6M", sex == "Male")) +
  scale_y_continuous(name = "Body Mass (g)",
                     breaks = seq(270, 470, 40),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(270, 470), clip = "off") +
  geom_vline(xintercept = c(1.5, 2.5), color = "grey90", lwd = 0.3) +
  theme(plot.margin = unit(c(8, 2, 2, 2), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "NMR_body_mass_6M_male.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 18M Female

```{r}
# 18M Female NMR Body Mass
plot_pre_post(x = filter(NMR, age == "18M", sex == "Female"), 
              pre = "pre_body_mass", post = "post_body_mass", 
              stats = filter(PRE_POST_STATS, response == "NMR Body Mass", 
                             age == "18M", sex == "Female")) +
  scale_y_continuous(name = "Body Mass (g)",
                     breaks = seq(160, 280, 20),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(155, 280), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "NMR_body_mass_18M_female.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 18M Male

```{r}
# 18M Male NMR Body Mass
plot_pre_post(x = filter(NMR, age == "18M", sex == "Male"), 
              pre = "pre_body_mass", post = "post_body_mass", 
              stats = filter(PRE_POST_STATS, response == "NMR Body Mass", 
                             age == "18M", sex == "Male")) +
  scale_y_continuous(name = "Body Mass (g)",
                     breaks = seq(270, 470, 40),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(270, 470), clip = "off") +
  theme(plot.margin = unit(c(8, 2, 2, 2), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "NMR_body_mass_18M_male.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```


# 1W, 2W: Terminal - Pre NMR Body Mass

Pre: body mass recorded on the same day as the NMR body composition measures in the 1W and 2W groups. Post: body mass recorded upon death (terminal body mass).

## 6M Female

```{r, fig.width=1.8}
# 6M Female terminal - NMR Body Mass
plot_pre_post(x = filter(BODY_MASSES, age == "6M", sex == "Female",
                         group %in% c("1W", "2W")), 
              pre = "nmr_pre_body_mass", post = "term_body_mass", 
              stats = filter(PRE_POST_STATS, 
                             response == "Term - NMR Pre Body Mass", 
                             age == "6M", sex == "Female")) +
  scale_y_continuous(name = "Body Mass (g)",
                     breaks = seq(160, 270, 20),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(155, 275), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "terminal_NMR_body_mass_6M_female.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 6M Male

```{r, fig.width=1.8}
# 6M Male terminal - NMR Body Mass
plot_pre_post(x = filter(BODY_MASSES, age == "6M", sex == "Male",
                         group %in% c("1W", "2W")), 
              pre = "nmr_pre_body_mass", post = "term_body_mass", 
              stats = filter(PRE_POST_STATS, 
                             response == "Term - NMR Pre Body Mass", 
                             age == "6M", sex == "Male")) +
  scale_y_continuous(name = "Body Mass (g)",
                     breaks = seq(300, 470, 40),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(295, 472), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "terminal_NMR_body_mass_6M_male.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 18M Female

```{r, fig.width=1.8}
# 18M Female terminal - NMR Body Mass
plot_pre_post(x = filter(BODY_MASSES, age == "18M", sex == "Female",
                         group %in% c("1W", "2W")), 
              pre = "nmr_pre_body_mass", post = "term_body_mass", 
              stats = filter(PRE_POST_STATS, 
                             response == "Term - NMR Pre Body Mass", 
                             age == "18M", sex == "Female")) +
  scale_y_continuous(name = "Body Mass (g)",
                     breaks = seq(160, 270, 20),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(155, 275), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "terminal_NMR_body_mass_18M_female.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 18M Male

```{r, fig.width=1.8}
# 18M Male terminal - NMR Body Mass
plot_pre_post(x = filter(BODY_MASSES, age == "18M", sex == "Male",
                         group %in% c("1W", "2W")), 
              pre = "nmr_pre_body_mass", post = "term_body_mass", 
              stats = filter(PRE_POST_STATS, 
                             response == "Term - NMR Pre Body Mass", 
                             age == "18M", sex == "Male")) +
  scale_y_continuous(name = "Body Mass (g)",
                     breaks = seq(300, 470, 40),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(295, 472), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "terminal_NMR_body_mass_18M_male.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```


# NMR Fat

Fat mass (g) recorded via NMR.

## 6M Female

```{r}
# 6M Female NMR Fat
plot_pre_post(x = filter(NMR, age == "6M", sex == "Female"), 
              pre = "pre_fat", post = "post_fat", 
              stats = filter(PRE_POST_STATS, response == "NMR Fat Mass", 
                             age == "6M", sex == "Female")) +
  scale_y_continuous(name = "NMR Fat Mass (g)",
                     breaks = seq(10, 60, 10),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(10, 64), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "NMR_fat_6M_female.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 6M Male

```{r}
# 6M Male NMR Fat
plot_pre_post(x = filter(NMR, age == "6M", sex == "Male"), 
              pre = "pre_fat", post = "post_fat", 
              stats = filter(PRE_POST_STATS, response == "NMR Fat Mass", 
                             age == "6M", sex == "Male")) +
  scale_y_continuous(name = "NMR Fat Mass (g)",
                     breaks = seq(20, 100, 20),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(18, 105), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "NMR_fat_6M_male.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 18M Female

```{r}
# 18M Female NMR Fat
plot_pre_post(x = filter(NMR, age == "18M", sex == "Female"), 
              pre = "pre_fat", post = "post_fat", 
              stats = filter(PRE_POST_STATS, response == "NMR Fat Mass", 
                             age == "18M", sex == "Female")) +
  scale_y_continuous(name = "NMR Fat Mass (g)",
                     breaks = seq(10, 60, 10),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(10, 64), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "NMR_fat_18M_female.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 18M Male

```{r}
# 18M Male NMR Fat
plot_pre_post(x = filter(NMR, age == "18M", sex == "Male"), 
              pre = "pre_fat", post = "post_fat", 
              stats = filter(PRE_POST_STATS, response == "NMR Fat Mass", 
                             age == "18M", sex == "Male")) +
  scale_y_continuous(name = "NMR Fat Mass (g)",
                     breaks = seq(20, 100, 20),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(18, 105), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "NMR_fat_18M_male.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```


# NMR Lean

Lean mass (g) recorded via NMR.

## 6M Female

```{r}
# 6M Female NMR Lean
plot_pre_post(x = filter(NMR, age == "6M", sex == "Female"), 
              pre = "pre_lean", post = "post_lean", 
              stats = filter(PRE_POST_STATS, response == "NMR Lean Mass", 
                             age == "6M", sex == "Female")) +
  scale_y_continuous(name = "NMR Lean Mass (g)",
                     breaks = seq(90, 150, 10),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(90, 153), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "NMR_lean_6M_female.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 6M Male

```{r}
# 6M Male NMR Lean
plot_pre_post(x = filter(NMR, age == "6M", sex == "Male"), 
              pre = "pre_lean", post = "post_lean", 
              stats = filter(PRE_POST_STATS, response == "NMR Lean Mass", 
                             age == "6M", sex == "Male")) +
  scale_y_continuous(name = "NMR Lean Mass (g)",
                     breaks = seq(150, 250, 20),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(149, 256), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "NMR_lean_6M_male.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 18M Female

```{r}
# 18M Female NMR Lean
plot_pre_post(x = filter(NMR, age == "18M", sex == "Female"), 
              pre = "pre_lean", post = "post_lean", 
              stats = filter(PRE_POST_STATS, response == "NMR Lean Mass", 
                             age == "18M", sex == "Female")) +
  scale_y_continuous(name = "NMR Lean Mass (g)",
                     breaks = seq(90, 150, 10),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(90, 153), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "NMR_lean_18M_female.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 18M Male

```{r}
# 18M Male NMR Lean
plot_pre_post(x = filter(NMR, age == "18M", sex == "Male"), 
              pre = "pre_lean", post = "post_lean", 
              stats = filter(PRE_POST_STATS, response == "NMR Lean Mass", 
                             age == "18M", sex == "Male")) +
  scale_y_continuous(name = "NMR Lean Mass (g)",
                     breaks = seq(150, 250, 20),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(149, 256), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "NMR_lean_18M_male.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```


# NMR % Fat

Fat mass (g) recorded via NMR divided by the body mass (g) recorded on the same day and then multiplied by 100%.

## 6M Female

```{r}
# 6M Female NMR % Fat
plot_pre_post(x = filter(NMR, age == "6M", sex == "Female"), 
              pre = "pre_fat_pct", post = "post_fat_pct", 
              stats = filter(PRE_POST_STATS, response == "NMR % Fat", 
                             age == "6M", sex == "Female")) +
  scale_y_continuous(name = "NMR % Fat Mass",
                     breaks = seq(6, 24, 4),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(6, 24), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "NMR_pct_fat_6M_female.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 6M Male

```{r}
# 6M Male NMR % Fat
plot_pre_post(x = filter(NMR, age == "6M", sex == "Male"), 
              pre = "pre_fat_pct", post = "post_fat_pct", 
              stats = filter(PRE_POST_STATS, response == "NMR % Fat", 
                             age == "6M", sex == "Male")) +
  scale_y_continuous(name = "NMR % Fat Mass",
                     breaks = seq(6, 22, 4),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(6, 22.2), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "NMR_pct_fat_6M_male.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 18M Female

```{r}
# 18M Female NMR % Fat
plot_pre_post(x = filter(NMR, age == "18M", sex == "Female"), 
              pre = "pre_fat_pct", post = "post_fat_pct", 
              stats = filter(PRE_POST_STATS, response == "NMR % Fat", 
                             age == "18M", sex == "Female")) +
  scale_y_continuous(name = "NMR % Fat Mass",
                     breaks = seq(6, 24, 4),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(6, 24), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "NMR_pct_fat_18M_female.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 18M Male

```{r}
# 18M Male NMR % Fat
plot_pre_post(x = filter(NMR, age == "18M", sex == "Male"), 
              pre = "pre_fat_pct", post = "post_fat_pct", 
              stats = filter(PRE_POST_STATS, response == "NMR % Fat", 
                             age == "18M", sex == "Male")) +
  scale_y_continuous(name = "NMR % Fat Mass",
                     breaks = seq(6, 22, 4),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(6, 22.2), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "NMR_pct_fat_18M_male.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```


# NMR % Lean

Lean mass (g) recorded via NMR divided by the body mass (g) recorded on the same day and then multiplied by 100%.

## 6M Female

```{r}
# 6M Female NMR % Lean
plot_pre_post(x = filter(NMR, age == "6M", sex == "Female"), 
              pre = "pre_lean_pct", post = "post_lean_pct", 
              stats = filter(PRE_POST_STATS, response == "NMR % Lean", 
                             age == "6M", sex == "Female")) +
  scale_y_continuous(name = "NMR % Lean Mass",
                     breaks = seq(50, 64, 2),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(50, 64), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "NMR_pct_lean_6M_female.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 6M Male

```{r}
# 6M Male NMR % Lean
plot_pre_post(x = filter(NMR, age == "6M", sex == "Male"), 
              pre = "pre_lean_pct", post = "post_lean_pct", 
              stats = filter(PRE_POST_STATS, response == "NMR % Lean", 
                             age == "6M", sex == "Male")) +
  scale_y_continuous(name = "NMR % Lean Mass",
                     breaks = seq(50, 64, 2),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(49.5, 64), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "NMR_pct_lean_6M_male.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 18M Female

```{r}
# 18M Female NMR % Lean
plot_pre_post(x = filter(NMR, age == "18M", sex == "Female"), 
              pre = "pre_lean_pct", post = "post_lean_pct", 
              stats = filter(PRE_POST_STATS, response == "NMR % Lean", 
                             age == "18M", sex == "Female")) +
  scale_y_continuous(name = "NMR % Lean Mass",
                     breaks = seq(50, 64, 2),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(50, 64), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "NMR_pct_lean_18M_female.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 18M Male

```{r}
# 18M Male NMR % Lean
plot_pre_post(x = filter(NMR, age == "18M", sex == "Male"), 
              pre = "pre_lean_pct", post = "post_lean_pct", 
              stats = filter(PRE_POST_STATS, response == "NMR % Lean", 
                             age == "18M", sex == "Male")) +
  scale_y_continuous(name = "NMR % Lean Mass",
                     breaks = seq(50, 64, 2),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(49.5, 64), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "NMR_pct_lean_18M_male.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```



# Absolute VO2max

Absolute VO$_2$max is calculated by multiplying relative VO$_2$max ($mL \cdot kg^{-1} \cdot min^{-1}$) by body mass (kg).

## 6M Female

```{r}
# 6M Female Absolute VO2max
plot_pre_post(x = filter(VO2MAX, age == "6M", sex == "Female"), 
              pre = "pre_vo2max_ml_min", post = "post_vo2max_ml_min", 
              stats = filter(PRE_POST_STATS, response == "Absolute VO2max", 
                             age == "6M") %>% 
                mutate(sex = "Female")) +
  scale_y_continuous(name = TeX("VO$_2$max (mL/min)"),
                     breaks = seq(10, 18, 2),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(10, 18), clip = "off") +
  theme(plot.margin = unit(c(6, 3, 3, 3), "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "absolute_VO2max_6M_female.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 6M Male

```{r}
# 6M Male Absolute VO2max
plot_pre_post(x = filter(VO2MAX, age == "6M", sex == "Male"), 
              pre = "pre_vo2max_ml_min", post = "post_vo2max_ml_min", 
              stats = filter(PRE_POST_STATS, response == "Absolute VO2max", 
                             age == "6M") %>% 
                mutate(sex = "Male")) +
  scale_y_continuous(name = TeX("VO$_2$max (mL/min)"),
                     breaks = seq(18, 26, 2),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(17.5, 27), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "absolute_VO2max_6M_male.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 18M Female

```{r, fig.width=1.8}
# 18M Female Absolute VO2max
plot_pre_post(x = filter(VO2MAX, age == "18M", sex == "Female"), 
              pre = "pre_vo2max_ml_min", post = "post_vo2max_ml_min", 
              stats = filter(PRE_POST_STATS, response == "Absolute VO2max", 
                             age == "18M") %>% 
                mutate(sex = "Female")) +
  scale_y_continuous(name = TeX("VO$_2$max (mL/min)"),
                     breaks = seq(10, 18, 2),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(10, 18), clip = "off") +
  theme(legend.position = "right",
        legend.direction = "vertical",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"),
        plot.margin = unit(c(6, 3, 3, 3), "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "absolute_VO2max_18M_female.pdf"),
       height = 1.4, width = 1.8, family = "ArialMT")
```

## 18M Male

```{r, fig.width=1.8}
# 18M Male Absolute VO2max
plot_pre_post(x = filter(VO2MAX, age == "18M", sex == "Male"), 
              pre = "pre_vo2max_ml_min", post = "post_vo2max_ml_min", 
              stats = filter(PRE_POST_STATS, response == "Absolute VO2max", 
                             age == "18M") %>% 
                mutate(sex = "Male")) +
  scale_y_continuous(name = TeX("VO$_2$max (mL/min)"),
                     breaks = seq(18, 26, 2),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(17.5, 27), clip = "off") +
  theme(legend.position = "right",
        legend.direction = "vertical",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "absolute_VO2max_18M_male.pdf"),
       height = 1.4, width = 1.8, family = "ArialMT")
```


# Relative VO2max

Relative VO$_2$max (mL/kg body mass/min).

## 6M Female

```{r}
# 6M Female Relative VO2max
plot_pre_post(x = filter(VO2MAX, age == "6M", sex == "Female"), 
              pre = "pre_vo2max_ml_kg_min", post = "post_vo2max_ml_kg_min", 
              stats = filter(PRE_POST_STATS, response == "Relative VO2max", 
                             age == "6M") %>% 
                mutate(sex = "Female")) +
  scale_y_continuous(name = TeX("VO$_2$max (mL/kg/min)"),
                     breaks = seq(50, 90, 10),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(44.5, 91), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "relative_VO2max_6M_female.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 6M Male

```{r}
# 6M Male Relative VO2max
plot_pre_post(x = filter(VO2MAX, age == "6M", sex == "Male"), 
              pre = "pre_vo2max_ml_kg_min", post = "post_vo2max_ml_kg_min", 
              stats = filter(PRE_POST_STATS, response == "Relative VO2max", 
                             age == "6M") %>% 
                mutate(sex = "Male")) +
  scale_y_continuous(name = TeX("VO$_2$max (mL/kg/min)"),
                     breaks = seq(40, 80, 10),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(40, 83), clip = "off")
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "relative_VO2max_6M_male.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 18M Female

```{r, fig.width=1.8}
# 18M Female Relative VO2max
plot_pre_post(x = filter(VO2MAX, age == "18M", sex == "Female"), 
              pre = "pre_vo2max_ml_kg_min", post = "post_vo2max_ml_kg_min", 
              stats = filter(PRE_POST_STATS, response == "Relative VO2max", 
                             age == "18M") %>% 
                mutate(sex = "Female")) +
  scale_y_continuous(name = TeX("VO$_2$max (mL/kg/min)"),
                     breaks = seq(50, 90, 10),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(44, 91), clip = "off") +
  theme(legend.position = "right",
        legend.direction = "vertical",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "relative_VO2max_18M_female.pdf"),
       height = 1.4, width = 1.8, family = "ArialMT")
```

## 18M Male

```{r, fig.width=1.8}
# 18M Male Relative VO2max
plot_pre_post(x = filter(VO2MAX, age == "18M", sex == "Male"), 
              pre = "pre_vo2max_ml_kg_min", post = "post_vo2max_ml_kg_min", 
              stats = filter(PRE_POST_STATS, response == "Relative VO2max", 
                             age == "18M") %>% 
                mutate(sex = "Male")) +
  scale_y_continuous(name = TeX("VO$_2$max (mL/kg/min)"),
                     breaks = seq(40, 80, 10),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(40, 83), clip = "off") +
  theme(legend.position = "right",
        legend.direction = "vertical",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "relative_VO2max_18M_male.pdf"),
       height = 1.4, width = 1.8, family = "ArialMT")
```


# Maximum Run Speed

Maximum run speed (m/min) reached during the VO$_2$max test.

## 6M Female

```{r}
# 6M Female max run speed
plot_pre_post(x = filter(VO2MAX, age == "6M", sex == "Female"), 
              pre = "pre_speed_max", post = "post_speed_max", 
              stats = filter(PRE_POST_STATS, response == "Maximum Run Speed", 
                             age == "6M", sex == "Female")) +
  scale_y_continuous(name = "Maximum Run Speed (m/min)",
                     breaks = seq(12.6, 36, 3.6)) +
  coord_cartesian(ylim = c(12.6, 36), clip = "off") +
  theme(plot.margin = unit(c(10, 2, 2, 2), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "max_run_speed_6M_female.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 6M Male

```{r}
# 6M Male max run speed
plot_pre_post(x = filter(VO2MAX, age == "6M", sex == "Male"), 
              pre = "pre_speed_max", post = "post_speed_max", 
              stats = filter(PRE_POST_STATS, response == "Maximum Run Speed", 
                             age == "6M", sex == "Male")) +
  scale_y_continuous(name = "Maximum Run Speed (m/min)",
                     breaks = seq(12.6, 36, 3.6)) +
  coord_cartesian(ylim = c(12.6, 36), clip = "off") +
  theme(plot.margin = unit(c(10, 2, 2, 2), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "max_run_speed_6M_male.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 18M Female

```{r}
# 18M Female max run speed
plot_pre_post(x = filter(VO2MAX, age == "18M", sex == "Female"), 
              pre = "pre_speed_max", post = "post_speed_max", 
              stats = filter(PRE_POST_STATS, response == "Maximum Run Speed", 
                             age == "18M", sex == "Female")) +
  scale_y_continuous(name = "Maximum Run Speed (m/min)",
                     breaks = seq(12.6, 36, 3.6)) +
  coord_cartesian(ylim = c(12.6, 36), clip = "off") +
  theme(plot.margin = unit(c(10, 2, 2, 2), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "max_run_speed_18M_female.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

## 18M Male

```{r}
# 18M Female max run speed
plot_pre_post(x = filter(VO2MAX, age == "18M", sex == "Male"), 
              pre = "pre_speed_max", post = "post_speed_max", 
              stats = filter(PRE_POST_STATS, response == "Maximum Run Speed", 
                             age == "18M", sex == "Male")) +
  scale_y_continuous(name = "Maximum Run Speed (m/min)",
                     breaks = seq(12.6, 36, 3.6)) +
  coord_cartesian(ylim = c(12.6, 36), clip = "off") +
  theme(plot.margin = unit(c(10, 2, 2, 2), units = "pt"))
```

```{r eval=save_plots}
ggsave(file.path("..", "..", "plots", "max_run_speed_18M_male.pdf"),
       height = 1.6, width = 1.8, family = "ArialMT")
```

