---
title: "Plots of post - pre differences"
output: 
  rmarkdown::html_document:
    code_folding: hide
    toc: true
    toc_depth: 2
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 2.1,
  fig.height = 1.6,
  out.height = "50%",
  out.width = "50%",
  dpi = 400,
  message = FALSE,
  warning = FALSE
)
```

```{r setup}
# Required packages
library(MotrpacRatTrainingPhysiologyData)
library(dplyr)
library(ggplot2)
library(latex2exp)
```


# NMR Weight {.tabset}

## 6M Female

```{r}
# 6M Female NMR Weight
plot_pre_post(x = filter(NMR, age == "6M", sex == "Female"), 
              pre = "pre_weight", post = "post_weight", 
              stats = filter(PRE_POST_STATS, response == "NMR Weight", 
                             age == "6M", sex == "Female"),
              scale = 1.15) +
  scale_y_continuous(name = "NMR Body Mass (g)",
                     breaks = seq(160, 240, 20),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(157, 240), clip = "off")

ggsave("../../plots/NMR_weight_6M_female.png", 
       height = 1.6, width = 2.1, dpi = 400)
```

## 6M Male

```{r}
# 6M Male NMR Weight
plot_pre_post(x = filter(NMR, age == "6M", sex == "Male"), 
              pre = "pre_weight", post = "post_weight", 
              stats = filter(PRE_POST_STATS, response == "NMR Weight", 
                             age == "6M", sex == "Male"),
              scale = 1.15) +
  scale_y_continuous(name = "NMR Body Mass (g)",
                     breaks = seq(260, 400, 40),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(260, 405), clip = "off")

ggsave("../../plots/NMR_weight_6M_male.png",
       height = 1.6, width = 2.1, dpi = 400)
```

## 18M Female

```{r}
# 18M Female NMR Weight
plot_pre_post(x = filter(NMR, age == "18M", sex == "Female"), 
              pre = "pre_weight", post = "post_weight", 
              stats = filter(PRE_POST_STATS, response == "NMR Weight", 
                             age == "18M", sex == "Female"),
              scale = 1.15) +
  scale_y_continuous(name = "NMR Body Mass (g)",
                     breaks = seq(200, 280, 20),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(200, 280), clip = "off")

ggsave("../../plots/NMR_weight_18M_female.png",
       height = 1.6, width = 2.1, dpi = 400)
```

## 18M Male

```{r}
# 18M Male NMR Weight
plot_pre_post(x = filter(NMR, age == "18M", sex == "Male"), 
              pre = "pre_weight", post = "post_weight", 
              stats = filter(PRE_POST_STATS, response == "NMR Weight", 
                             age == "18M", sex == "Male"),
              scale = 1.15) +
  scale_y_continuous(name = "NMR Body Mass (g)",
                     breaks = seq(360, 460, 20),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(356, 475), clip = "off")

ggsave("../../plots/NMR_weight_18M_male.png",
       height = 1.6, width = 2.1, dpi = 400)
```


# 1W, 2W: Terminal - Pre NMR Weight {.tabset}

## 6M Female

```{r, fig.width=1.8}
# 6M Female terminal - NMR Weight
plot_pre_post(x = filter(WEIGHTS, age == "6M", sex == "Female",
                         group %in% c("1W", "2W")), 
              pre = "nmr_pre_weight", post = "term_weight", 
              stats = filter(PRE_POST_STATS, 
                             response == "Term - NMR Pre Weight", 
                             age == "6M", sex == "Female"),
              scale = 1.15) +
  scale_y_continuous(name = "Body Mass (g)",
                     breaks = seq(170, 210, 10),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(170, 210), clip = "off")

ggsave("../../plots/terminal_NMR_weight_6M_female.png",
       height = 1.6, width = 1.8, dpi = 400)
```

## 6M Male

```{r, fig.width=1.8}
# 6M Male terminal - NMR Weight
plot_pre_post(x = filter(WEIGHTS, age == "6M", sex == "Male",
                         group %in% c("1W", "2W")), 
              pre = "nmr_pre_weight", post = "term_weight", 
              stats = filter(PRE_POST_STATS, 
                             response == "Term - NMR Pre Weight", 
                             age == "6M", sex == "Male"),
              scale = 1.15) +
  scale_y_continuous(name = "Body Mass (g)",
                     breaks = seq(300, 440, 40),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(295, 440), clip = "off")

ggsave("../../plots/terminal_NMR_weight_6M_male.png",
       height = 1.6, width = 1.8, dpi = 400)
```

## 18M Female

```{r, fig.width=1.8}
# 18M Female terminal - NMR Weight
plot_pre_post(x = filter(WEIGHTS, age == "18M", sex == "Female",
                         group %in% c("1W", "2W")), 
              pre = "nmr_pre_weight", post = "term_weight", 
              stats = filter(PRE_POST_STATS, 
                             response == "Term - NMR Pre Weight", 
                             age == "18M", sex == "Female"),
              scale = 1.15) +
  scale_y_continuous(name = "Body Mass (g)",
                     breaks = seq(200, 260, 20),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(194, 274), clip = "off")

ggsave("../../plots/terminal_NMR_weight_18M_female.png",
       height = 1.6, width = 1.8, dpi = 400)
```

## 18M Male

```{r, fig.width=1.8}
# 18M Male terminal - NMR Weight
plot_pre_post(x = filter(WEIGHTS, age == "18M", sex == "Male",
                         group %in% c("1W", "2W")), 
              pre = "nmr_pre_weight", post = "term_weight", 
              stats = filter(PRE_POST_STATS, 
                             response == "Term - NMR Pre Weight", 
                             age == "18M", sex == "Male"),
              scale = 1.15) +
  scale_y_continuous(name = "Body Mass (g)",
                     breaks = seq(360, 460, 20),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(355, 472), clip = "off")

ggsave("../../plots/terminal_NMR_weight_18M_male.png",
       height = 1.6, width = 1.8, dpi = 400)
```



# NMR Fat {.tabset}

## 6M Female

```{r}
# 6M Female NMR Fat
plot_pre_post(x = filter(NMR, age == "6M", sex == "Female"), 
              pre = "pre_fat", post = "post_fat", 
              stats = filter(PRE_POST_STATS, response == "NMR Fat Mass", 
                             age == "6M", sex == "Female"),
              scale = 1.15) +
  scale_y_continuous(name = "NMR Fat Mass (g)",
                     breaks = seq(10, 35, 5),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(10, 37), clip = "off")

ggsave("../../plots/NMR_fat_6M_female.png",
       height = 1.6, width = 2.1, dpi = 400)
```


## 6M Male

```{r}
# 6M Male NMR Fat
plot_pre_post(x = filter(NMR, age == "6M", sex == "Male"), 
              pre = "pre_fat", post = "post_fat", 
              stats = filter(PRE_POST_STATS, response == "NMR Fat Mass", 
                             age == "6M", sex == "Male"),
              scale = 1.15) +
  scale_y_continuous(name = "NMR Fat Mass (g)",
                     breaks = seq(20, 80, 10),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(18, 80), clip = "off")

ggsave("../../plots/NMR_fat_6M_male.png",
       height = 1.6, width = 2.1, dpi = 400)
```

## 18M Female

```{r}
# 18M Female NMR Fat
plot_pre_post(x = filter(NMR, age == "18M", sex == "Female"), 
              pre = "pre_fat", post = "post_fat", 
              stats = filter(PRE_POST_STATS, response == "NMR Fat Mass", 
                             age == "18M", sex == "Female"),
              scale = 1.15) +
  scale_y_continuous(name = "NMR Fat Mass (g)",
                     breaks = seq(30, 60, 10),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(28, 64), clip = "off")

ggsave("../../plots/NMR_fat_18M_female.png",
       height = 1.6, width = 2.1, dpi = 400)
```

## 18M Male

```{r}
# 18M Male NMR Fat
plot_pre_post(x = filter(NMR, age == "18M", sex == "Male"), 
              pre = "pre_fat", post = "post_fat", 
              stats = filter(PRE_POST_STATS, response == "NMR Fat Mass", 
                             age == "18M", sex == "Male"),
              scale = 1.15) +
  scale_y_continuous(name = "NMR Fat Mass (g)",
                     breaks = seq(40, 100, 10),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(40, 105), clip = "off")

ggsave("../../plots/NMR_fat_18M_male.png",
       height = 1.6, width = 2.1, dpi = 400)
```


# NMR Lean {.tabset}

## 6M Female

```{r}
# 6M Female NMR Lean
plot_pre_post(x = filter(NMR, age == "6M", sex == "Female"), 
              pre = "pre_lean", post = "post_lean", 
              stats = filter(PRE_POST_STATS, response == "NMR Lean Mass", 
                             age == "6M", sex == "Female"),
              scale = 1.15) +
  scale_y_continuous(name = "NMR Lean Mass (g)",
                     breaks = seq(90, 130, 10),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(90, 135), clip = "off")

ggsave("../../plots/NMR_lean_6M_female.png",
       height = 1.6, width = 2.1, dpi = 400)
```

## 6M Male

```{r}
# 6M Male NMR Lean
plot_pre_post(x = filter(NMR, age == "6M", sex == "Male"), 
              pre = "pre_lean", post = "post_lean", 
              stats = filter(PRE_POST_STATS, response == "NMR Lean Mass", 
                             age == "6M", sex == "Male"),
              scale = 1.15) +
  scale_y_continuous(name = "NMR Lean Mass (g)")

ggsave("../../plots/NMR_lean_6M_male.png",
       height = 1.6, width = 2.1, dpi = 400)
```

## 18M Female

```{r}
# 18M Female NMR Lean
plot_pre_post(x = filter(NMR, age == "18M", sex == "Female"), 
              pre = "pre_lean", post = "post_lean", 
              stats = filter(PRE_POST_STATS, response == "NMR Lean Mass", 
                             age == "18M", sex == "Female"),
              scale = 1.15) +
  scale_y_continuous(name = "NMR Lean Mass (g)")

ggsave("../../plots/NMR_lean_18M_female.png",
       height = 1.6, width = 2.1, dpi = 400)
```

## 18M Male

```{r}
# 18M Male NMR Lean
plot_pre_post(x = filter(NMR, age == "18M", sex == "Male"), 
              pre = "pre_lean", post = "post_lean", 
              stats = filter(PRE_POST_STATS, response == "NMR Lean Mass", 
                             age == "18M", sex == "Male"),
              scale = 1.15) +
  scale_y_continuous(name = "NMR Lean Mass (g)")

ggsave("../../plots/NMR_lean_18M_male.png",
       height = 1.6, width = 2.1, dpi = 400)
```


# NMR % Fat {.tabset}

## 6M Female

```{r}
# 6M Female NMR % Fat
plot_pre_post(x = filter(NMR, age == "6M", sex == "Female"), 
              pre = "pre_fat_pct", post = "post_fat_pct", 
              stats = filter(PRE_POST_STATS, response == "NMR % Fat", 
                             age == "6M", sex == "Female"),
              scale = 1.15) +
  scale_y_continuous(name = "NMR % Fat Mass",
                     breaks = seq(6, 18, 2),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(6, 18), clip = "off")

ggsave("../../plots/NMR_pct_fat_6M_female.png",
       height = 1.6, width = 2.1, dpi = 400)
```

## 6M Male

```{r}
# 6M Male NMR % Fat
plot_pre_post(x = filter(NMR, age == "6M", sex == "Male"), 
              pre = "pre_fat_pct", post = "post_fat_pct", 
              stats = filter(PRE_POST_STATS, response == "NMR % Fat", 
                             age == "6M", sex == "Male"),
              scale = 1.15) +
  scale_y_continuous(name = "NMR % Fat Mass",
                     breaks = seq(6, 20, 2),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(6, 20.5), clip = "off")

ggsave("../../plots/NMR_pct_fat_6M_male.png",
       height = 1.6, width = 2.1, dpi = 400)
```

## 18M Female

```{r}
# 18M Female NMR % Fat
plot_pre_post(x = filter(NMR, age == "18M", sex == "Female"), 
              pre = "pre_fat_pct", post = "post_fat_pct", 
              stats = filter(PRE_POST_STATS, response == "NMR % Fat", 
                             age == "18M", sex == "Female"),
              scale = 1.15) +
  scale_y_continuous(name = "NMR % Fat Mass",
                     breaks = seq(14, 24, 2),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(13.7, 24), clip = "off")

ggsave("../../plots/NMR_pct_fat_18M_female.png",
       height = 1.6, width = 2.1, dpi = 400)
```

## 18M Male

```{r}
# 18M Male NMR % Fat
plot_pre_post(x = filter(NMR, age == "18M", sex == "Male"), 
              pre = "pre_fat_pct", post = "post_fat_pct", 
              stats = filter(PRE_POST_STATS, response == "NMR % Fat", 
                             age == "18M", sex == "Male"),
              scale = 1.15) +
  scale_y_continuous(name = "NMR % Fat Mass",
                     breaks = seq(12, 22, 2),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(11.5, 22.2), clip = "off")

ggsave("../../plots/NMR_pct_fat_18M_male.png",
       height = 1.6, width = 2.1, dpi = 400)
```


# NMR % Lean {.tabset}

## 6M Female

```{r}
# 6M Female NMR % Lean
plot_pre_post(x = filter(NMR, age == "6M", sex == "Female"), 
              pre = "pre_lean_pct", post = "post_lean_pct", 
              stats = filter(PRE_POST_STATS, response == "NMR % Lean", 
                             age == "6M", sex == "Female"),
              scale = 1.15) +
  scale_y_continuous(name = "NMR % Lean Mass",
                     breaks = seq(52, 64, 2),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(51.9, 64), clip = "off")

ggsave("../../plots/NMR_pct_lean_6M_female.png",
       height = 1.6, width = 2.1, dpi = 400)
```

## 6M Male

```{r}
# 6M Male NMR % Lean
plot_pre_post(x = filter(NMR, age == "6M", sex == "Male"), 
              pre = "pre_lean_pct", post = "post_lean_pct", 
              stats = filter(PRE_POST_STATS, response == "NMR % Lean", 
                             age == "6M", sex == "Male"),
              scale = 1.15) +
  scale_y_continuous(name = "NMR % Lean Mass",
                     breaks = seq(52, 64, 2),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(52, 64), clip = "off")

ggsave("../../plots/NMR_pct_lean_6M_male.png",
       height = 1.6, width = 2.1, dpi = 400)
```

## 18M Female

```{r}
# 18M Female NMR % Lean
plot_pre_post(x = filter(NMR, age == "18M", sex == "Female"), 
              pre = "pre_lean_pct", post = "post_lean_pct", 
              stats = filter(PRE_POST_STATS, response == "NMR % Lean", 
                             age == "18M", sex == "Female"),
              scale = 1.15) +
  scale_y_continuous(name = "NMR % Lean Mass",
                     breaks = seq(50, 60, 2),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(50, 60), clip = "off")

ggsave("../../plots/NMR_pct_lean_18M_female.png",
       height = 1.6, width = 2.1, dpi = 400)
```

## 18M Male

```{r}
# 18M Male NMR % Lean
plot_pre_post(x = filter(NMR, age == "18M", sex == "Male"), 
              pre = "pre_lean_pct", post = "post_lean_pct", 
              stats = filter(PRE_POST_STATS, response == "NMR % Lean", 
                             age == "18M", sex == "Male"),
              scale = 1.15) +
  scale_y_continuous(name = "NMR % Lean Mass",
                     breaks = seq(50, 57, 1),
                     expand = expansion(mult = 5e-3),
                     labels = seq(50, 57, 1)) +
  coord_cartesian(ylim = c(49.5, 57), clip = "off")

ggsave("../../plots/NMR_pct_lean_18M_male.png",
       height = 1.6, width = 2.1, dpi = 400)
```



# Absolute VO2max {.tabset}

## 6M Female

```{r}
# 6M Female Absolute VO2max
plot_pre_post(x = filter(VO2MAX, age == "6M", sex == "Female"), 
              pre = "pre_vo2max_ml_min", post = "post_vo2max_ml_min", 
              stats = filter(PRE_POST_STATS, response == "Absolute VO2max", 
                             age == "6M") %>% 
                mutate(sex = "Female"),
              scale = 1.15) +
  scale_y_continuous(name = TeX("VO$_2$max (mL/min)"),
                     breaks = seq(10, 18, 2),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(10, 18), clip = "off")

ggsave("../../plots/absolute_VO2max_6M_female.png",
       height = 1.6, width = 2.1, dpi = 400)
```

## 6M Male

```{r}
# 6M Male Absolute VO2max
plot_pre_post(x = filter(VO2MAX, age == "6M", sex == "Male"), 
              pre = "pre_vo2max_ml_min", post = "post_vo2max_ml_min", 
              stats = filter(PRE_POST_STATS, response == "Absolute VO2max", 
                             age == "6M") %>% 
                mutate(sex = "Male"),
              scale = 1.15) +
  scale_y_continuous(name = TeX("VO$_2$max (mL/min)"),
                     breaks = seq(18, 26, 2),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(17.8, 27), clip = "off")

ggsave("../../plots/absolute_VO2max_6M_male.png",
       height = 1.6, width = 2.1, dpi = 400)
```

## 18M Female

```{r, fig.width=1.8}
# 18M Female Absolute VO2max
plot_pre_post(x = filter(VO2MAX, age == "18M", sex == "Female"), 
              pre = "pre_vo2max_ml_min", post = "post_vo2max_ml_min", 
              stats = filter(PRE_POST_STATS, response == "Absolute VO2max", 
                             age == "18M") %>% 
                mutate(sex = "Female"),
              scale = 1.15) +
  scale_y_continuous(name = TeX("VO$_2$max (mL/min)")) +
  theme(legend.position = "right",
        legend.direction = "vertical",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"))

ggsave("../../plots/absolute_VO2max_18M_female.png",
       height = 1.4, width = 2.1, dpi = 400)
```

## 18M Male

```{r, fig.width=1.8}
# 18M Male Absolute VO2max
plot_pre_post(x = filter(VO2MAX, age == "18M", sex == "Male"), 
              pre = "pre_vo2max_ml_min", post = "post_vo2max_ml_min", 
              stats = filter(PRE_POST_STATS, response == "Absolute VO2max", 
                             age == "18M") %>% 
                mutate(sex = "Male"),
              scale = 1.15) +
  scale_y_continuous(name = TeX("VO$_2$max (mL/min)"),
                     breaks = seq(18, 24, 2),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(17.5, 24), clip = "off") +
  theme(legend.position = "right",
        legend.direction = "vertical",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"))

ggsave("../../plots/absolute_VO2max_18M_male.png",
       height = 1.4, width = 2.1, dpi = 400)
```


# Relative VO2max {.tabset}

## 6M Female

```{r}
# 6M Female Relative VO2max
plot_pre_post(x = filter(VO2MAX, age == "6M", sex == "Female"), 
              pre = "pre_vo2max_ml_kg_min", post = "post_vo2max_ml_kg_min", 
              stats = filter(PRE_POST_STATS, response == "Relative VO2max", 
                             age == "6M") %>% 
                mutate(sex = "Female"),
              scale = 1.15) +
  scale_y_continuous(name = TeX("VO$_2$max (mL/kg/min)"),
                     breaks = seq(60, 90, 5),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(60, 91), clip = "off")

ggsave("../../plots/relative_VO2max_6M_female.png",
       height = 1.6, width = 2.1, dpi = 400)
```

## 6M Male

```{r}
# 6M Male Relative VO2max
plot_pre_post(x = filter(VO2MAX, age == "6M", sex == "Male"), 
              pre = "pre_vo2max_ml_kg_min", post = "post_vo2max_ml_kg_min", 
              stats = filter(PRE_POST_STATS, response == "Relative VO2max", 
                             age == "6M") %>% 
                mutate(sex = "Male"),
              scale = 1.15) +
  scale_y_continuous(name = TeX("VO$_2$max (mL/kg/min)"),
                     breaks = seq(50, 85, 5),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(50, 85), clip = "off")

ggsave("../../plots/relative_VO2max_6M_male.png",
       height = 1.6, width = 2.1, dpi = 400)
```

## 18M Female

```{r, fig.width=1.8}
# 18M Female Relative VO2max
plot_pre_post(x = filter(VO2MAX, age == "18M", sex == "Female"), 
              pre = "pre_vo2max_ml_kg_min", post = "post_vo2max_ml_kg_min", 
              stats = filter(PRE_POST_STATS, response == "Relative VO2max", 
                             age == "18M") %>% 
                mutate(sex = "Female"),
              scale = 1.15) +
  scale_y_continuous(name = TeX("VO$_2$max (mL/kg/min)")) +
  theme(legend.position = "right",
        legend.direction = "vertical",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"))

ggsave("../../plots/relative_VO2max_18M_female.png",
       height = 1.4, width = 2.1, dpi = 400)
```

## 18M Male

```{r, fig.width=1.8}
# 18M Male Relative VO2max
plot_pre_post(x = filter(VO2MAX, age == "18M", sex == "Male"), 
              pre = "pre_vo2max_ml_kg_min", post = "post_vo2max_ml_kg_min", 
              stats = filter(PRE_POST_STATS, response == "Relative VO2max", 
                             age == "18M") %>% 
                mutate(sex = "Male"),
              scale = 1.15) +
  scale_y_continuous(name = TeX("VO$_2$max (mL/kg/min)"),
                     breaks = seq(40, 65, 5),
                     expand = expansion(mult = 5e-3)) +
  coord_cartesian(ylim = c(40, 65), clip = "off") +
  theme(legend.position = "right",
        legend.direction = "vertical",
        legend.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"))

ggsave("../../plots/relative_VO2max_18M_male.png",
       height = 1.4, width = 2.1, dpi = 400)
```


# Maximum Run Speed {.tabset}

## 6M Female

```{r}
# 6M Female max run speed
plot_pre_post(x = filter(VO2MAX, age == "6M", sex == "Female"), 
              pre = "pre_speed_max", post = "post_speed_max", 
              stats = filter(PRE_POST_STATS, response == "Maximum Run Speed", 
                             age == "6M", sex == "Female"),
              scale = 1.15) +
  scale_y_continuous(name = "Maximum Run Speed (m/min)",
                     breaks = seq(21.6, 36, 3.6))

ggsave("../../plots/max_run_speed_6M_female.png",
       height = 1.6, width = 2.1, dpi = 400)
```


## 6M Male

```{r}
# 6M Male max run speed
plot_pre_post(x = filter(VO2MAX, age == "6M", sex == "Male"), 
              pre = "pre_speed_max", post = "post_speed_max", 
              stats = filter(PRE_POST_STATS, response == "Maximum Run Speed", 
                             age == "6M", sex == "Male"),
              scale = 1.15) +
  scale_y_continuous(name = "Maximum Run Speed (m/min)",
                     breaks = seq(18, 36, 3.6))

ggsave("../../plots/max_run_speed_6M_male.png",
       height = 1.6, width = 2.1, dpi = 400)
```

## 18M Female

```{r}
# 18M Female max run speed
plot_pre_post(x = filter(VO2MAX, age == "18M", sex == "Female"), 
              pre = "pre_speed_max", post = "post_speed_max", 
              stats = filter(PRE_POST_STATS, response == "Maximum Run Speed", 
                             age == "18M", sex == "Female"),
              scale = 1.15) +
  scale_y_continuous(name = "Maximum Run Speed (m/min)",
                     breaks = seq(16.2, 36, 3.6))

ggsave("../../plots/max_run_speed_18M_female.png",
       height = 1.6, width = 2.1, dpi = 400)
```

## 18M Male

```{r}
# 18M Female max run speed
plot_pre_post(x = filter(VO2MAX, age == "18M", sex == "Male"), 
              pre = "pre_speed_max", post = "post_speed_max", 
              stats = filter(PRE_POST_STATS, response == "Maximum Run Speed", 
                             age == "18M", sex == "Male"),
              scale = 1.15) +
  scale_y_continuous(name = "Maximum Run Speed (m/min)",
                     breaks = seq(12.6, 36, 3.6))

ggsave("../../plots/max_run_speed_18M_male.png",
       height = 1.6, width = 2.1, dpi = 400)
```


